---
title: "Historical funding levels of DoJ and FTC"
author: "Sima Biondi"
date: "9/22/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(tidyverse)
library(data.table)
library(readxl)
library(writexl)
library(here)
library(scales)
library(xlsx)

fig.path = here::here("figs/agency budget")
options(warn = -1)
```

# Loading data 

Loading:
- DOJ and FTC Congressional appropriations data
- DOJ and FTC Merger Filing fee data
- FTC Budget and personnel allocation broken down by Mission
- Historical CPI index and GDP per capita

```{r read data}

# DOJ data  ---
## Name: DOJ Congressional appropriation and merger filing data
## Description: DOJ Congressional appropriations and merger filing fees starting in 1903 
## Source: DOJ Antitrust Division website
## Note: The DOJ merger filing fees are also the FTC's merger filing fees
doj_df_read = read_excel("data/doj_atr-appropriation-figures1017.xls", sheet = "data")
names(doj_df_read) = c("year", "doj_direct_appro_amt", "doj_filing_fee_amt", "doj_total_amt", "notes")

# FTC data ---
## Name: FTC Congressional appropriations data
## Description: FTC Congressional appropriations data
## Source: Handcoded from Congressional Budget documents retrieved through FRASER. Copies of the original source materials can be found in "ftc appropriation docs / cong_appro". 
ftc_df_read = read_excel("data/ftc_appro.xlsx")


## Name: FTC fiscal and personnel budget by Mission
## Description: The FTC's budget broken down by type of Mission (ie. Promoting Competition (antitrust), Consumer Protection). 
## Source: Handcoded data from FTC Annual Reports. Copies of the original source materials can be found in *. 
ftc_breakdown_df_read = read_excel("data/ftc appropriations docs/ftc_financial_reports.xlsx")

# Data for inflation and GDP per capita adjustments ---
## Name: Inflation index
## Description: Loading two versions of the same inflation indexes from two different sources. One (from 1913) is an annual index and the other (starting in 1947) is a quarterly index.
## Sources: Bureau of Labor Statistics' CPI Index (U) website and FRED online portal
inflation_df_1913 = read_excel("data/CPI_index_u.xlsx")
inflation_df_1913 = inflation_df_1913 %>%
  filter(year < 1947)
inflation_df_1947 = read.table("http://research.stlouisfed.org/fred2/data/CPIAUCSL.txt",
             skip = 54, header = TRUE)

## Name: Historical GDP per capita data
## Description: US historical GDP per capita data
## Source: Maddison project (*)
real_gdp_per_capita_data = read_excel("data/gdp-per-capita-maddison-2020.xlsx", sheet = "data")

```
# Cleaning the data
```{r clean doj data}
# Cleaning DOJ Congressional appropriation and merger filing data
## Description: Multiplying monetary values by 1K because the original data was conveyed in thousands of dollars.
doj_df_clean = doj_df_read %>%
  select(-notes) %>%
  mutate(across(ends_with("amt"), ~ .x*1000)) 

```

```{r clean ftc data}
# Merging FTC Congressional appropriations data with DOJ appropriations data; creating additional FTC data from existing FTC/DOJ data
# Description: 
  ## Loading FTC and DOJ Cong. appropriations data then joining by appropriations year
  ## Creating a column for FTC merger filing fees by replicating DOJ merger filing fees because they are identical by law. 
  ## Creating a total FTC budget data column by combining the FTC's merger filing fee and Congressional appropriations amounts
ftc_df_clean = ftc_df_read %>%
  left_join(doj_df_clean) %>%
  rename(ftc_filing_fee_amt = doj_filing_fee_amt) %>%
  mutate(ftc_total_amt = case_when(is.na(ftc_filing_fee_amt) ~ ftc_appro_amt,
                                   T ~ ftc_appro_amt + ftc_filing_fee_amt)) %>%
  select(year, ftc_total_amt, ftc_appro_amt, ftc_filing_fee_amt)
```


```{r clean inflation data}
# Description: combining two versions of the CPI U (inflation index)
  ## Transform a quarterly index into an annual index 
  ## Add values from the annual index (starts in 1913)
  ## Arrange values by year
inflation_df = inflation_df_1947 %>%
  mutate(year = year(DATE)) %>%
  group_by(year) %>%
  summarise(cpi = mean(VALUE)) %>%
  bind_rows(., inflation_df_1913) %>%
  arrange(year) 
```


```{r clean real GDP per capita}
# Description:
  ## Removing unnecessary variables to the analysis
  ## Renaming variables for later merging
  ## Removing rows for later merging 
real_GDP_per_capita_df = real_gdp_per_capita_data %>%
  select(-Code, -`145446-annotations`, -Entity) %>%
  rename(year = Year, `Real GDP per capita` = `GDP per capita` ) %>%
  filter(year >= 1913)
```


# Combining data sources
```{r}
# Description: merging/reshaping agency budget data
  ## Merge FTC and DOJ data by year 
  ## Reshape the data longer

agency_budgets = doj_df_clean %>%
  left_join(ftc_df_clean) %>%
  pivot_longer(!year, names_to = "budget_id", values_to = "budget_allocated_amt")

```



```{r graph agency budgets without adjustments}
# Description: Plotting un-adjusted agency total budget amounts
  ## Filter for years after 1930 and before 2019 to capture the full range of years represented of the data
  ## Filter for the DOJ and FTC's total budget amounts (as opposed to Congressional appropriations or merger filing fees)
  ## Rename data values and plot with a simple scatter

agency_budgets %>%
  filter(year > 1930 & year < 2019) %>%
  filter(budget_id == "doj_total_amt" | 
           budget_id == "ftc_total_amt") %>%
  filter(!is.na(budget_allocated_amt)) %>%
  mutate(budget_id = case_when(budget_id == "doj_total_amt" ~ "DOJ antitrust division",
                                T ~ "FTC")) %>%
  ggplot(., aes(x = year, y = budget_allocated_amt, 
                group = budget_id, color = budget_id)) + geom_point() + 
  labs(colour = "Agency", title = "Budgets over time: DoJ Antitrust division and FTC") + ylab("Nominal dollars") + scale_y_continuous(label = comma)

ggsave(path = fig.path, "agency_budget_no_adj.png")

```


# Adjusting for inflation (total budget)
```{r adjusting for inflation}

# Description: creating inflation adjustment for 2011 dollars
  ## Create a year-by-year adjustment factor by dividing each CPI value by the 2011 value

inflation_df = inflation_df %>%
  mutate(cpi_of_2011 = filter(inflation_df, year == 2011)$cpi) %>%
  mutate(adj_factor = cpi/cpi_of_2011)


# Description: Plotting inflation adjusted total agency budgets 
  ## Merge inflation data with budget data and filter for relevant years/budget components
  ## Adjust the budget allocated amount by dividing it by the inflation adjustment factor calculated above 
  ## Rename data values and plot data with a simple scatter
agency_budgets %>%
  full_join(., inflation_df, by = "year") %>%
  filter(year > 1930 & year < 2019) %>%
  filter(budget_id == "doj_total_amt" | 
           budget_id == "ftc_total_amt") %>%
  mutate(budget_allocated_amt_adj = budget_allocated_amt/adj_factor) %>%
  filter(!is.na(budget_allocated_amt_adj)) %>%
  mutate(budget_id = case_when(budget_id == "doj_total_amt" ~ "DOJ antitrust division",
                                T ~ "FTC")) %>%
  ggplot(., aes(x = year, y = budget_allocated_amt_adj, 
                group = budget_id, color = budget_id)) + geom_point() + 
                  labs(colour = "Agency", title = "Budgets over time: DoJ Antitrust division and FTC") + 
                  ylab("Dollars (inflation adjusted, 2011)") + 
                  scale_y_continuous(label = comma) 

ggsave(path = fig.path, "agency_budget_inflation_adj.png")

  
```

# Adjusting for inflation and real GDP per capita
```{r adjusting for inflation_df and real GDP per capita}

# Description: create real GDP per capita adjustment factor 
  ## Create a year-by-year adjustment factor by dividing each real GDP per capita value by the 2011 value
base_year_val_rGDPpc = real_GDP_per_capita_df$`Real GDP per capita`[real_GDP_per_capita_df$year == 2011]
real_GDP_per_capita_df = real_GDP_per_capita_df %>%
  mutate(rGDPpc_base_2011 =  (`Real GDP per capita`)/base_year_val_rGDPpc) 

# Description: Plotting inflation and real GDP per capita adjusted total agency budgets with a linear trendline
  ## Merge inflation and real GDP per capita adjustment factors into agency budget data by year
  ## Filter for relevant years/budget components
  ## Adjust the budget allocated amount by dividing it by the inflation/real GDP per capita adjustment factor calculated above 
  ## Rename data values and plot data with a scatter plot and a linear trend line with a break in 1975 (to divide high/low enforcement periods)
agency_budgets %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  filter(year > 1930 & year < 2019) %>%
  filter(budget_id == "doj_total_amt" | 
           budget_id == "ftc_total_amt") %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  mutate(time_period = case_when(year <= 1975 ~ "pre", T ~ "post")) %>% 
  mutate(test = case_when(time_period == "pre" & budget_id == "doj_total_amt" ~ 1,
                          time_period == "post" & budget_id == "doj_total_amt" ~ 2,
                          time_period == "pre" & budget_id == "ftc_total_amt" ~ 3,
                          T ~ 4)) %>%
  filter(!is.na(budget_allocated_amt_adj)) %>%
  mutate(budget_id = case_when(budget_id == "doj_total_amt" ~ "DOJ antitrust division",
                                T ~ "FTC")) %>% 
  ggplot(., aes(x = year, y = budget_allocated_amt_adj, 
                group = budget_id, color = budget_id)) + geom_point() + 
                  labs(colour = "Agency", title = "Budgets over time: DoJ Antitrust division and FTC") + 
                  ylab("Dollars (inflation and real GDP per capita adjusted, 2011)") + 
                  scale_y_continuous(label = comma) + geom_smooth(method = "lm", aes(group = test))

ggsave(path = fig.path, "agency_budget_point_trend.png")


```

# Decomposing budget data
```{r}

# Description: cleaning/reshaping FTC budget breakdown data

ftc_breakdown_df = ftc_breakdown_df_read %>%
  select(year, competitionFunds) %>%
  pivot_longer(!year, names_to = "budget_id", values_to = "budget_allocated_amt")

```


```{r}

# Description: Visualizing overlap between agency Congressional appropriations and merger filing fees
agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  filter(budget_id == "doj_total_amt" | budget_id == "competitionFunds" | 
           str_detect(budget_id, "filing_fee_amt")) %>%
   filter(year > 1989 & year < 2021) %>%
    mutate(agency_id = case_when(str_detect(budget_id, "doj") ~ "DoJ Antitrust",
                               T ~ "FTC's Competition Bureau"),
         budget_id_type = case_when(str_detect(budget_id, "fee") ~ "Filing fee",
                               T ~ "Total budget")) %>%
## plotting  
  ggplot(aes(x = year, y = budget_allocated_amt_adj, color = budget_id_type)) +
  geom_col(position = "identity", alpha = 0.2) + 
  facet_wrap(vars(agency_id)) + 
  theme_minimal() + 
  labs(colour = "Funding source", title = "Budgets over time: DoJ Antitrust division and FTC",
     caption = "Source: FTC Annual Reports and Congressional Budget Justification Summary",
     y = "Dollars (inflation and real GDP per capita adjusted, 2011)",
     x = "Year") + 
  scale_y_continuous(label = label_number(suffix = " M", scale = 1e-6)) 

ggsave(path = fig.path, "agency_budget_decompose_bar.png")


  
  
  
  
  
```



```{r}

agency_budgets_breakdown_df = agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  pivot_wider(names_from = budget_id, values_from = budget_allocated_amt) %>%
  mutate(ftcCompApproNotFines = case_when(is.na(ftc_filing_fee_amt) ~ competitionFunds,
                                           ftc_filing_fee_amt > competitionFunds ~
                                             competitionFunds,
                                           ftc_filing_fee_amt < competitionFunds ~
                                             competitionFunds,
                                           T ~ competitionFunds)) %>%
  pivot_longer(!year, names_to = "budget_id", values_to = "budget_allocated_amt") %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  filter(year > 1930 & year < 2019) %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  filter(!is.na(budget_allocated_amt_adj) & year > 1952) %>%
  
  filter(budget_id != "doj_total_amt" & budget_id != "ftc_total_amt" &
           budget_id != "ftc_appro_amt" & budget_id != "competitionFunds") %>%
  mutate(budget_id = case_when(budget_id == "doj_direct_appro_amt" ~ "DOJ Congressional appropriation",
                               budget_id == "doj_filing_fee_amt" ~ "DOJ filing fee revenue",
                               budget_id == "ftcCompApproNotFines" ~ 
                                 "FTC 'Maintaining Competition' Congressional appropriation",
                               budget_id == "ftc_filing_fee_amt" ~ "FTC filing fee revenue")) %>%
  mutate(agency_id = case_when(str_detect(budget_id, "FTC") ~ "FTC",
                               T ~ "DOJ")) %>%
    mutate(budget_id = case_when(str_detect(budget_id, "filing fee") ~ "Filing fee revenue",
                                 T ~ "Congressional allocation"))

agency_budgets_breakdown_df %>%
  rename(`Funding source` = budget_id) %>%
  ggplot(., aes(x = year, y = budget_allocated_amt_adj, fill= `Funding source`)) +
    geom_col() +
    facet_wrap(~agency_id) +
                  labs(colour = "Funding source", title = "Budgets over time: DoJ Antitrust division and FTC",
                       caption = "Source: FTC Annual Reports and Congressional Budget Justification Summary") + 
                  ylab("Dollars (inflation and real GDP per capita adjusted, 2011)") + 
                  scale_y_continuous(label = label_number(suffix = " M", scale = 1e-6)) +
  theme_minimal()
ggsave(path = fig.path, "agency_budget_decompose_bar.png")

agency_budgets_breakdown_df %>%
  filter(year == 2010)

```



```{r}

agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  filter(year > 1952 & year < 2019) %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  filter(!is.na(budget_allocated_amt_adj)) %>%
  filter(budget_id != "doj_total_amt" & budget_id != "ftc_total_amt" &
           budget_id != "ftc_appro_amt") %>%
  mutate(budget_id = case_when(budget_id == "doj_direct_appro_amt" ~ "DOJ Congressional appropriation",
                               budget_id == "doj_filing_fee_amt" ~ "DOJ filing fee revenue",
                               budget_id == "competitionFunds" ~ 
                                 "FTC 'Maintaining Competition' Congressional appropriation",
                               budget_id == "ftc_filing_fee_amt" ~ "FTC filing fee revenue")) %>%
  mutate(agency_id = case_when(str_detect(budget_id, "FTC") ~ "FTC",
                               T ~ "DOJ")) %>%
    mutate(budget_id = case_when(str_detect(budget_id, "filing fee") ~ "Filing fee revenue",
                                 T ~ budget_id)) %>%
  rename(`Funding source` = budget_id) %>%
  ggplot(., aes(x = year, y = budget_allocated_amt_adj, color= `Funding source`, group = `Funding source`)) +
    geom_point() +
        labs(colour = "Funding source", title = "Budgets over time: DoJ Antitrust division and FTC") +
                  ylab("Dollars (inflation and real GDP per capita adjusted, 2011)") + 
                  scale_y_continuous(label = comma)

ggsave(path = fig.path, "agency_budget_decompose_point.png")



```


```{r}


agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  filter(year > 1952 & year < 2021) %>%
  filter(budget_id == "doj_total_amt" | budget_id ==  "competitionFunds") %>%
  mutate(budget_id = recode(budget_id, "doj_total_amt" = "doj_total_amt",
                                        "competitionFunds" = "ftc_total_amt")) %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  mutate(agency_id = case_when(str_detect(budget_id, "doj") ~ "DoJ",
                               T ~ "FTC")) %>%
  mutate(budget_id = case_when(str_detect(budget_id, "filing fee") ~ "Filing fee revenue",
                                 T ~ budget_id)) %>%
  mutate(time_period = case_when(year <= 1975 ~ "pre", T ~ "post")) %>% 
  mutate(test = case_when(time_period == "pre" & agency_id == "DoJ" ~ 1,
                          time_period == "post" & agency_id == "DoJ" ~ 2,
                          time_period == "pre" & agency_id == "FTC" ~ 3,
                          T ~ 4)) %>%
  ggplot(., aes(x = year, y = budget_allocated_amt_adj, 
                group = agency_id, color = agency_id)) + geom_point() + 
                  labs(colour = "Agency", title = "Budgets over time: DoJ Antitrust division and FTC",
                       y = "Dollars (inflation and real GDP \nper capita adjusted, 2011)",
                       x = "Year",
                       caption = "Source: Annual Reports of the FTC, the FTC's annual Congressional budget request, and DOJ website") + 
                  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) + 
  geom_smooth(method = "lm", aes(group = test)) +
  theme_minimal() +
  theme(legend.position = "bottom")
  ggsave(path = fig.path, "agency_budget_decompose_line_1975.png")
  
  
  agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  filter(year > 1952 & year < 2021) %>%
  filter(budget_id == "doj_total_amt" | budget_id ==  "competitionFunds") %>%
  mutate(budget_id = recode(budget_id, "doj_total_amt" = "doj_total_amt",
                                        "competitionFunds" = "ftc_total_amt")) %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  mutate(agency_id = case_when(str_detect(budget_id, "doj") ~ "DoJ",
                               T ~ "FTC")) %>%
  mutate(budget_id = case_when(str_detect(budget_id, "filing fee") ~ "Filing fee revenue",
                                 T ~ budget_id)) %>%
  mutate(time_period = case_when(year <= 1980 ~ "pre", T ~ "post")) %>% 
  mutate(test = case_when(time_period == "pre" & agency_id == "DoJ" ~ 1,
                          time_period == "post" & agency_id == "DoJ" ~ 2,
                          time_period == "pre" & agency_id == "FTC" ~ 3,
                          T ~ 4)) %>%
  ggplot(., aes(x = year, y = budget_allocated_amt_adj, 
                group = agency_id, color = agency_id)) + geom_point() + 
                  labs(colour = "Agency", title = "Budgets over time: DoJ Antitrust division and FTC",
                       y = "Dollars (inflation and real GDP \nper capita adjusted, 2011)",
                       x = "Year",
                       caption = "Source: Annual Reports of the FTC, the FTC's annual Congressional budget request, and DOJ website") + 
                  scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6)) + 
  geom_smooth(method = "lm", aes(group = test)) +
  theme_minimal() +
  theme(legend.position = "bottom")
    ggsave(path = fig.path, "agency_budget_decompose_line_1980.png")


  
```



# FTC FTEs

```{r}
ftc_breakdown_df_read %>%
  select(year, competitionFTE) %>%
  pivot_longer(!year) %>%
  filter(!is.na(value)) %>%
  ggplot() + geom_point(aes(x = year, y = value)) +
    labs(x = "Year", y = "FTEs", title = "FTC's 'Maintaining Competition' mission's FTEs")
ggsave(path = fig.path, "ftc_ftes_competition.png")

ftc_breakdown_df_read %>%
  select(year, competitionFTE, consumerProtectionFTE) %>%
  pivot_longer(!year, names_to = "type_FTE") %>%
  filter(!is.na(value)) %>%
  mutate(type_FTE = recode(type_FTE, 'consumerProtectionFTE' = 'Consumer Protection ',
                           'competitionFTE' = 'Maintaining Competition')) %>%
  mutate(Mission = type_FTE) %>%
  ggplot() + geom_point(aes(x = year, y = value, color = Mission)) +
    labs(x = "Year", y = "FTEs", title = "FTC's mission's FTEs",
         caption = "FTC's Annual Reports and Congressional Budget Justifications") + theme_minimal() +
    theme(legend.position = "bottom")
ggsave(path = fig.path, "ftc_ftes_competition_and_consumer.png")

```


# Flourish data


## Agency budgets overall
```{r}


agencyBudgetAdjusted = agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  filter(year > 1952 & year < 2021) %>%
  filter(budget_id == "doj_total_amt" | budget_id ==  "competitionFunds") %>%
  mutate(budget_id = recode(budget_id, "doj_total_amt" = "doj_total_amt",
                                        "competitionFunds" = "ftc_total_amt")) %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  mutate(agency_id = case_when(str_detect(budget_id, "doj") ~ "DoJ",
                               T ~ "FTC")) %>%
  mutate(budget_id = case_when(str_detect(budget_id, "filing fee") ~ "Filing fee revenue",
                                 T ~ budget_id)) %>%
  select(agency_id, budget_allocated_amt_adj, year) %>%
  pivot_wider(names_from = agency_id, values_from = budget_allocated_amt_adj) %>%
  rowwise() %>%
  mutate(mergers = runif(1, min = 74416005/2, max = 199437871/2))

setwd("data/final figures")  
write_excel_csv(agencyBudgetAdjusted, "7_agencyBudgets.xlsx")
  




  
```

## Composition of agency budgets
```{r}
agencyBudgetCompositionAdjusted_1 = agency_budgets %>%
  bind_rows(ftc_breakdown_df) %>%
  full_join(., inflation_df, by = "year") %>%
  left_join(., real_GDP_per_capita_df, by = "year") %>%
  mutate(budget_allocated_amt_adj = (budget_allocated_amt/adj_factor)/rGDPpc_base_2011) %>%
  filter(budget_id == "doj_total_amt" | budget_id == "competitionFunds" | 
           str_detect(budget_id, "filing_fee_amt")) %>%
   filter(year > 1989 & year < 2019) %>%
    mutate(agency_id = case_when(str_detect(budget_id, "doj") ~ "DoJ Antitrust",
                               T ~ "FTC's Competition Bureau"),
         budget_id_type = case_when(str_detect(budget_id, "fee") ~ "Filing fee",
                               T ~ "Antitrust budget")) %>%
  select(year, agency_id, budget_allocated_amt_adj, budget_id_type) 

agencyBudgetCompositionAdjusted =  agencyBudgetCompositionAdjusted_1%>%
  group_by(year, agency_id) %>%
  summarise(year = first(year), agency_id = first(agency_id), 
            budget_id_type = "overlap",
            budget_allocated_amt_adj = min(budget_allocated_amt_adj)) %>%
  bind_rows(agencyBudgetCompositionAdjusted_1) %>%
  ungroup %>%
  pivot_wider(names_from = budget_id_type, values_from = budget_allocated_amt_adj)

 
setwd("data/final figures")  
write_excel_csv(agencyBudgetCompositionAdjusted, "8_agencyBudgetsComposition.xlsx")
  

```

## FTC FTEs
```{r}
ftcFTEs = ftc_breakdown_df_read %>%
  select(year, competitionFTE, consumerProtectionFTE) %>%
  pivot_longer(!year, names_to = "type_FTE") %>%
  filter(!is.na(value)) %>%
  mutate(type_FTE = recode(type_FTE, 'consumerProtectionFTE' = 'Consumer Protection ',
                           'competitionFTE' = 'Maintaining Competition')) %>%
  rename(Mission = type_FTE) %>%
  pivot_wider(names_from = Mission, values_from = value)

setwd("data/final figures")  
write_excel_csv(ftcFTEs, "9_ftcFTEs.xlsx")
  


```


