---
title: "ATE salary data figures"
output:
  pdf_document: default
  html_document:
    df_print: paged
date: "8/27/2021"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(gghighlight)
library(readxl)
library(dplyr)
library(scales)

fig.path = here::here("figs/salaries")

```


```{r read data}
df = read_excel("data/gov_law_salary_df_adjusted.xlsx")
df_inflation = read_excel("data/gov_law_salary_df_inflation_adjusted.xlsx")
```




# Compensation over time with salaries adjusted for inflation (dot plot, line)

```{r graphs (inflation only combo)}
df_inflation %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      ggtitle("Compensation over time (adjusted for inflation)") +
      ylab("Dollars (adjusted, 2011)") +
      scale_y_continuous(label = comma)  +
      labs(colour = "Position") 

ggsave(path = fig.path, "salaries_inflation_scatter.png")


df_inflation %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      geom_line() +
      ggtitle("Compensation over time (adjusted for inflation)") +
      scale_y_continuous(label = comma, name = "Dollars (adjusted, 2011)") +
      labs(colour = "Position") 

ggsave(path = fig.path, "salaries_inflation_line.png")

```


# Compensation over time with salaries adjusted for inflation, without President (dot plot, line)

```{r graphs (inflation only combo and without President)}
df_inflation %>%
  filter(personnel_type != "President") %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      ggtitle("Compensation over time (adjusted for inflation)") +
      ylab("Dollars (adjusted, 2011)") +
      scale_y_continuous(label = comma)  +
      labs(colour = "Position") 
ggsave(path = fig.path, "salaries_inflation_without_pres_scatter.png")


df_inflation_declutter = df_inflation %>%
  filter(personnel_type != "President" & personnel_type != "Chief Justice" &
           personnel_type != "Federal Reserve Chair") 

  
df_inflation_declutter %>%
  ggplot() +
    geom_line(data = filter(df_inflation_declutter, !(personnel_type == "DC median house price" & year < 1987)), 
              aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
    geom_point(data = filter(df_inflation_declutter, !(personnel_type == "DC median house price" & year < 1987)), 
              aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type),
              size = 0.25) +
    geom_point(data = filter(df_inflation, personnel_type == "DC median house price" & year < 1987), 
               aes(x = year, y = salary_adj, group = personnel_type), size = 0.25, color = "yellow4") +
    ggtitle("Compensation over time (adjusted for inflation)") +
    scale_y_continuous(label = label_number(suffix = " M", scale = 1e-6),
                       name = "Dollars (adjusted, 2011)") +
    labs(colour = "Position") + theme_minimal() +
    theme(legend.position = "bottom")

ggsave(path = fig.path, "salaries_inflation_without_pres_line.png", 
       width = 12, height = 6)

```


# Compensation over time with salaries adjusted for inflation (faceted, all positions)
```{r graphs facet with president (inflation only)}
df_inflation %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = factor(personnel_type))) +
      geom_point(size = 0.25) + 
      gghighlight(min(salary_adj) > 0,  use_direct_label = FALSE)+ 
      theme_minimal() +
      facet_wrap(~ personnel_type) +
      ggtitle("Compensation over time (adjusted for inflation)") +
      scale_y_continuous(label = comma, name = "Dollars (adjusted, 2011)") +
      theme(legend.position = "none")

ggsave(path = fig.path, "salaries_inflation_inflation_faceted.png")

```



# Compensation over time with salaries adjusted for inflation and per capita GDP (dot, line)

```{r graphs (combo)}
df %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      ylab("Dollars (adjusted, 2011)") +
      scale_y_continuous(label = comma)  +
      labs(colour = "Position") 

ggsave(path = fig.path, "salaries_inflation_rGDPpc_scatter.png")


df %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      geom_line() +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      scale_y_continuous(label = comma, name = "Dollars (adjusted, 2011)") +
      labs(colour = "Position") 

ggsave(path = fig.path, "salaries_inflation_rGDPpc_line.png")

```

# Compensation over time with salaries adjusted for inflation and per capita GDP, without President (dot, line)

```{r graphs (combo and without President)}
df %>%
  filter(personnel_type != "President") %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      ylab("Dollars (adjusted, 2011)") +
      scale_y_continuous(label = comma)  +
      labs(colour = "Position")
ggsave(path = fig.path, "salaries_inflation_rGDPpc_without_pres_scatter.png")


df %>%
  filter(personnel_type != "President" & personnel_type != "Appeals court judge" & 
            personnel_type != "Federal Reserve Chair" &
            personnel_type != "Chief Justice") %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
      geom_point(size = 0.25) +
      geom_line() +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      scale_y_continuous(labels = label_number(suffix = " M", scale = 1e-6), name = "Dollars (adjusted, 2011)") +
      labs(colour = "Position") + theme_minimal() +
      theme(legend.position = "bottom")



df_declutter = df %>%
  filter(personnel_type != "President" & 
           personnel_type != "Federal Reserve Chair" &
           personnel_type != "Chief Justice")
  
df_declutter %>%
  ggplot() +
    geom_line(data = filter(df_declutter, !(personnel_type == "DC median house price" & year < 1987)), 
              aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type)) +
    geom_point(data = filter(df_declutter, !(personnel_type == "DC median house price" & year < 1987)), 
              aes(x = year, y = salary_adj, group = personnel_type, color = personnel_type),
              size = 0.25) +
    geom_point(data = filter(df, personnel_type == "DC median house price" & year < 1987), 
               aes(x = year, y = salary_adj, group = personnel_type), size = 0.25, color = "yellow4") +
      ggtitle("Compensation over time \n(adjusted for inflation and real GDP per capita growth)") + 
      scale_y_continuous(label = label_number(suffix = " M", scale = 1e-6),
                         name = "Dollars (inflation and real GDP \nper capita adjusted, 2011)") +
      labs(colour = "Position", y = "Year") + theme_minimal() +
      theme(legend.position = "bottom")
ggsave(path = fig.path, "salaries_inflation_rGDPpc_without_pres_line.png",
       width = 12, height = 6)


```


# Compensation over time with salaries adjusted for inflation and per capita GDP (faceted, all positions)
```{r graphs facet with president}
df %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = factor(personnel_type))) +
      geom_point(size = 0.25) + 
      gghighlight(min(salary_adj) > 0,  use_direct_label = FALSE)+ 
      theme_minimal() +
      facet_wrap(~ personnel_type) +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      scale_y_continuous(label = comma, name = "Dollars (adjusted, 2011)") +
      theme(legend.position = "none")

ggsave(path = fig.path, "salaries_inflation_rGDPpc_faceted.png")

```

# Compensation over time with salaries adjusted for inflation and per capita GDP (faceted, without President)

```{r graphs facet without president}
df %>%
  filter(personnel_type != "President") %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = factor(personnel_type))) +
      geom_point(size = 0.25) + 
      gghighlight(min(salary_adj) > 0, use_direct_label = FALSE) + 
      theme_minimal() +
      facet_wrap(~ personnel_type) +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      scale_y_continuous(label = comma, name = "Dollars (adjusted, 2011)") +
      theme(legend.position = "none")

ggsave(path = fig.path, "salaries_inflation_rGDPpc_without_pres_faceted.png")


```


# Compensation over time with salaries adjusted for inflation and per capita GDP (starting in 1940)

```{r graph facet starting in 1940}
df %>%
  filter(year > 1939) %>%
  ggplot(., aes(x = year, y = salary_adj, group = personnel_type, color = factor(personnel_type))) +
      geom_point(size = 0.25) + 
      gghighlight(min(salary_adj) > 0, use_direct_label = FALSE) + 
      theme_minimal() +
      facet_wrap(~ personnel_type) +
      ggtitle("Compensation over time (adjusted for inflation and real GDP per capita)") +
      scale_y_continuous(label = comma, name = "Dollars (adjusted, 2011)") +
      theme(legend.position = "none", panel.spacing.x = unit(4, "mm"))

ggsave(path = fig.path, "salaries_inflation_rGDPpc_start_1940_faceted.png")


```
# Flourish figure
```{r}


personnelSalaries = df_inflation_declutter %>%
  select(year, personnel_type, salary_adj) %>%
  pivot_wider(names_from = personnel_type, values_from =  salary_adj, values_fn = mean)

setwd("data/final figures")  
write_excel_csv(personnelSalaries, "19_personnelSalaries.xlsx")


```



