---
title: "ATE project - data tables"
author: "Sima Biondi"
date: "4/7/2022"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = F, message = F)
options(warn = -1)
library(ggplot2)
library(dplyr)
library(tidyr)
library(finalfit)
library(readxl)
library(writexl)
library(forcats)
library(stringr)
library(kableExtra)
library(lemon)
library(flextable)
library(usethis)
library(readr)
library(markdown)
```

```{r test}
#rmarkdown::render("previous_positions.Rmd", "html", params = params)

#source('previous_positions.R')

source(knitr::purl("previous_positions.Rmd", quiet=TRUE))
#source(knitr::purl("sct_ate_analysis.Rmd", quiet=TRUE))


```

## Nominations tables
### Nomination data split by president

```{r }
noms_by_pres_tbl %>%
  flextable() %>%
  autofit() %>%
  fit_to_width(5.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Duration of nomination hearings (in minutes)", 
                            "Substantive antitrust discussions?",
                            "Substantive attitudes toward enforcement"),
                 colwidths = c(2, 2, 3, 3)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
  flextable::vline(part = "all", j = 2) %>%
  flextable::vline(part = "all", j = 4) %>%
  flextable::vline(part = "all", j = 7) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 


```

\newpage


### Nomination data split by type of position and president
```{r}
noms_by_pres_and_pos %>%
  flextable() %>%
  autofit() %>%
  fit_to_width(5.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Duration of nomination hearings (in minutes)", 
                            "Substantive antitrust discussions?",
                            "Substantive attitudes toward enforcement"),
                 colwidths = c(3, 2, 3, 3)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
  flextable::vline(part = "all", j = 3) %>%
  flextable::vline(part = "all", j = 5) %>%
  flextable::vline(part = "all", j = 8) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
```



### Nomination data split by type of position
```{r}
noms_by_position %>%
  flextable() %>%
  autofit() %>%
  fit_to_width(5.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Duration of nomination hearings (in minutes)", 
                            "Substantive antitrust discussions?",
                            "Substantive attitudes toward enforcement"),
                 colwidths = c(2, 2, 3, 3)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
  flextable::vline(part = "all", j = 2) %>%
  flextable::vline(part = "all", j = 4) %>%
  flextable::vline(part = "all", j = 7) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
```

### Nomination data split by decade
```{r}
noms_by_decade %>%
  flextable() %>%
    autofit() %>%
  fit_to_width(5.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Duration of nomination hearings (in minutes)", 
                            "Substantive antitrust discussions?",
                            "Substantive attitudes toward enforcement"),
                 colwidths = c(2, 2, 3, 3)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
  flextable::vline(part = "all", j = 2) %>%
  flextable::vline(part = "all", j = 4) %>%
  flextable::vline(part = "all", j = 7) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
  
```
### Nomination data split by party in control of Senate
```{r}
noms_by_partyControl %>%
  flextable() %>%
  autofit() %>%
  fit_to_width(5.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Duration of nomination hearings (in minutes)", 
                            "Substantive antitrust discussions?",
                            "Substantive attitudes toward enforcement"),
                 colwidths = c(2, 2, 3, 3)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
  flextable::vline(part = "all", j = 2) %>%
  flextable::vline(part = "all", j = 4) %>%
  flextable::vline(part = "all", j = 7) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
```

### Nomination data split by era and party in control of Senate
```{r}
noms_by_era_partyControl %>%
  flextable() %>%
    autofit() %>%
  fit_to_width(6.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Duration of nomination hearings (in minutes)", 
                            "Substantive antitrust discussions?",
                            "Substantive attitudes toward enforcement"),
                 colwidths = c(3, 2, 3, 3)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
  flextable::vline(part = "all", j = 3) %>%
  flextable::vline(part = "all", j = 5) %>%
  flextable::vline(part = "all", j = 8) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
  
```









## SCT data analysis tables



```{r read}
sc_judge_read = read_excel("data/Supreme Court Chart.xlsx", sheet = "Business friendliness")

bf_scores_read = read_csv("data/Business2020_sb1.csv")


# ------ Datasets to create antitrust case dataset
#additional_cases_antitrust_read = read_csv("data/additional_cases_antitrust_sc_changed.csv")
#brannon_ginsburg_df_read = read_excel("data/brannon_ginsburg_data.xlsx")

```

```{r clean SC judges Excel}
sc_judge = sc_judge_read %>%
  mutate(year_oath = format(`Date of Oath`, "%Y")) %>%
  mutate(across(c(CC_endorse, WSJ_endorse),  na_if, "Unavailable")) %>%
  mutate(era = case_when(year_oath > 1975 ~ "Low enforcement",
                         T ~ "High enforcement")) %>%
  mutate(across(.cols = ends_with("endorse"), .fns = ~ case_when(str_detect(., "y") ~ 1, 
                                                                 T ~ 0))) %>%
  mutate(name_edit = `Last Name, First Name`) %>%
  mutate(last_name = str_extract(name_edit, "^[a-zA-Z]*")) %>%
  mutate(row_num = 1:n()) %>%
  mutate(initials = str_extract_all(name_edit, "[A-Z]")[row_num]) %>%
  mutate(middle_initial = as.character(purrr::map(initials, 3))) %>%
  mutate(first_initial = as.character(purrr::map(initials, 2))) %>%
  mutate(across(middle_initial:first_initial, ~ replace(., . == "NULL", NA))) %>%
  mutate(name_final = case_when(is.na(middle_initial) ~ paste(first_initial, last_name, sep = ""),
                                T ~ paste(first_initial, middle_initial, last_name, sep = ""))) %>%
  mutate(name_final = case_when(name_edit == "O'Connor, Sandra Day" ~ "SDOConnor",
                                name_edit == "Harlan, John Marshall" ~ "JHarlan2",
                                name_edit == "Hughes, Charles Evans" ~ "CEHughes2",
                                T ~ name_final)) %>%
  rename(justiceName = name_final)

```

```{r BF and BF_NYT scores from Epstein data}

justice_bf_scores  = bf_scores_read %>%
  filter(term > 1951) %>%
  filter(BusinessLitigant == "1. business is Petitioner OR respondent") %>%
  group_by(justiceName, JVoteForBusiness) %>%
  summarise(votes = n()) %>%
  filter(!is.na(JVoteForBusiness)) %>%
  pivot_wider(names_from = JVoteForBusiness, values_from = votes) %>%
  mutate(total_votes = `j vote against business` + `j vote for business`,
         score = round(`j vote for business`/(`j vote against business` + `j vote for business`), 3)) %>%
  mutate(score_type = "bf") %>%
  rename(`pro-enforcement` = `j vote against business`,
         `anti-enforcement` = `j vote for business`) %>%
  filter(justiceName %in% sc_judge$justiceName) 

justice_bf_nyt_scores = bf_scores_read %>%
    filter(term > 1951) %>%
  filter(BusinessLitigant == "1. business is Petitioner OR respondent" &
           nytSalience == 1) %>%
  group_by(justiceName, JVoteForBusiness) %>%
  summarise(votes = n()) %>%
  filter(!is.na(JVoteForBusiness)) %>%
  pivot_wider(names_from = JVoteForBusiness, values_from = votes) %>%
    replace(is.na(.), 0) %>%
  mutate(total_votes = `j vote against business` + `j vote for business`,
         score = round(`j vote for business`/(`j vote against business` + `j vote for business`), 3)) %>%
  mutate(score_type = "bf_nyt") %>%
  rename(`pro-enforcement` = `j vote against business`,
         `anti-enforcement` = `j vote for business`) %>%
  filter(justiceName %in% sc_judge$justiceName) 

```



### Summary mean of overall business friendliness score (bf) and business friendliness score of business-related cases appearing in the NYT (nyt)

### Inclusive of all cases:
```{r}

t_test_bf_scores = bind_rows(justice_bf_scores,justice_bf_nyt_scores) %>%
  left_join(select(sc_judge, Party, justiceName)) %>%
  select(Party, score, score_type) %>%
  group_by(Party, score_type) %>%
  summarise(val = list(score)) %>%
  pivot_wider(names_from = Party, values_from = val) %>%
  group_by(score_type) %>%
  mutate(p_value = round(t.test(unlist(D), unlist(R))$p.value, 2),
         t_value = round(t.test(unlist(D), unlist(R))$statistic, 2),
         D_mean = round(mean(unlist(D), na.rm = T), 2),
         D_sd = round(sd(unlist(D), na.rm = T), 2),
         R_mean = round(mean(unlist(R)), 2),
         R_sd = round(sd(unlist(R)), 2),
         df = round(t.test(unlist(D), unlist(R))$parameter, 2),      
         CI_lower = round(t.test(unlist(D), unlist(R))$conf.int[[1]], 2),
         CI_upper = round(t.test(unlist(D), unlist(R))$conf.int[[2]], 2),
         meanDiff = R_mean-D_mean) %>%
  select(score_type, D_mean, D_sd, R_mean, R_sd,
         t_value, df, p_value, CI_lower, CI_upper) %>%
  mutate(score_type = ifelse(score_type == "bf", "Business-friendliness", 
                             "Business-friendliness (NYT cases)")) %>%
  rename(`Type of score` = score_type,
         `Mean (D)` = D_mean,
         `SD (D)` = D_sd,
         `Mean (R)` = R_mean,
         `SD (R)` = R_sd,
         `T` = t_value,
         `Significance` = p_value,
         `Lower` = CI_lower,
         `Upper` = CI_upper) 

t_test_bf_scores %>%
  flextable() %>%
  autofit() %>%
  fit_to_width(6.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "Democrats", 
                            "Republicans",
                            "T-test",
                            "Confidence interval"),
                 colwidths = c(1, 2, 2, 3, 2)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
 # flextable::vline(part = "all", j = 2) %>%
  #flextable::vline(part = "all", j = 4) %>%
  #flextable::vline(part = "all", j = 7) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
```



### Grouped by era:

High enforcement: 1945-1975.
Low enforcement: 1976-2019.

```{r}

t_test_bf_scores_era =  bind_rows(justice_bf_scores,justice_bf_nyt_scores) %>%
  left_join(select(sc_judge, era, justiceName)) %>%
  
  select(era, score, score_type, justiceName) %>%  
  group_by(era, score_type) %>%
  summarise(val = list(score)) %>%
  pivot_wider(names_from = "era", values_from = "val") %>%
  group_by(score_type) %>%
    mutate(p_value = round(t.test(unlist(`High enforcement`), 
                                  unlist(`Low enforcement`))$p.value, 2),
         t_value = round(t.test(unlist(`High enforcement`), 
                                unlist(`Low enforcement`))$statistic, 2),
         highEnforcement_mean = round(mean(unlist(`High enforcement`), na.rm = T), 2),
         highEnforcement_sd = round(sd(unlist(`High enforcement`), na.rm = T), 2),
         lowEnforcement_mean = round(mean(unlist(`Low enforcement`)), 2),
         lowEnforcement_sd = round(sd(unlist(`Low enforcement`)), 2),
         df = round(t.test(unlist(`High enforcement`), 
                           unlist(`Low enforcement`))$parameter, 2),      
         CI_lower = round(t.test(unlist(`High enforcement`), 
                                 unlist(`Low enforcement`))$conf.int[[1]], 2),
         CI_upper = round(t.test(unlist(`High enforcement`), 
                                 unlist(`Low enforcement`))$conf.int[[2]], 2),
         meanDiff = lowEnforcement_mean-highEnforcement_mean) %>%
  select(score_type, 
         highEnforcement_mean, highEnforcement_sd, lowEnforcement_mean, lowEnforcement_sd,
         t_value, df, p_value, CI_lower, CI_upper) %>%
  mutate(score_type = ifelse(score_type == "bf", "Business-friendliness", 
                              "Business-friendliness (NYT cases)")) %>%
  rename(`Type of score` = score_type,
         `Mean (high)` = highEnforcement_mean,
         `SD (high)` = highEnforcement_sd,
         `Mean (low)` = lowEnforcement_mean,
         `SD (low)` = lowEnforcement_sd,
         `T` = t_value,
         `Significance` = p_value,
         `Lower` = CI_lower,
         `Upper` = CI_upper) 

t_test_bf_scores_era %>%
   flextable() %>%
  autofit() %>%
  fit_to_width(6.5) %>%
  add_header_row(top = T,
                 values = c(" ",
                            "High enforcement", 
                            "Low enforcement",
                            "T-test",
                            "Confidence interval"),
                 colwidths = c(1, 2, 2, 3, 2)) %>%
  theme_booktabs() %>%
  flextable::align(., align = "center", part = "all") %>%
  flextable::font(fontname = "Times New Roman", part = "all") %>%
  fontsize(i = 1, size = 10, part = "header") %>%   
 # flextable::vline(part = "all", j = 2) %>%
  #flextable::vline(part = "all", j = 4) %>%
  #flextable::vline(part = "all", j = 7) %>%
  flextable::italic(i = 1, italic = TRUE, part = "header") 
```


