---
title: "Polling analysis"
author: "Sima Biondi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F)
library(dplyr)
library(tidyr)
library(stringr)
library(ggplot2)
library(rvest)
library(formatR)
library(xlsx)
fig.path = here::here("figs/final draft/polls")

```

## Load data

```{r read Roper data}

setwd("polls/roper polling data/overall")

dir = as.array(list.files())
dfRoper_load = data.frame()

for(i in 1:length(dir)){
  temp = read.csv(dir[i], header = T, check.names = F) %>%
    mutate(QuestionID = as.character(QuestionID),
           RespPct = as.character(RespPct), 
           file = as.character(dir[i]),
           questionType = "overall")
  dfRoper_load = bind_rows(dfRoper_load, temp)
}

```

```{r read Gallup data}
page = read_html("https://news.gallup.com/poll/1597/Confidence-Institutions.aspx")

html_tbls = page %>%
  html_elements("table") %>%
  html_table()

```

```{r read Roper business power data}

setwd("polls/roper polling data/business power")

dir = as.array(list.files())
dfRoperBusiness_load = data.frame()

for(i in 1:length(dir)){
  temp = read.csv(dir[i], header = T, check.names = T) %>%
    mutate(QuestionID = as.character(QuestionID),
           RespPct = as.character(RespPct), 
           file = as.character(dir[i]),
           questionType = "powerDC")
  dfRoperBusiness_load = bind_rows(dfRoperBusiness_load, temp)
}


```


```{r read Roper large company regulation data}

setwd("polls/roper polling data/controlling large companies - GE survey")

dir = as.array(list.files())
dfRoperGE_load = data.frame()

for(i in 1:length(dir)){
  temp = read.csv(dir[i], header = T, check.names = T) %>%
    mutate(QuestionID = as.character(QuestionID),
           RespPct = as.character(RespPct), 
           file = as.character(dir[i]),
           questionType = "largeCompanyRegulation")
  dfRoperGE_load = bind_rows(dfRoperGE_load, temp)
}



dfRoperGE_load = dfRoperGE_load  %>%
  mutate(AntitrustDirection = case_when(str_detect(RespTxt, "more") ~ "pro",
                                        str_detect(RespTxt, "less") ~ "anti",
                                        T ~ "ambig")) 


```


## Clean data
``` {r clean Roper}
dfRoper = dfRoper_load %>%
  bind_rows(dfRoperBusiness_load) %>%
  bind_rows(dfRoperGE_load) %>%
  mutate(century = case_when(as.integer(str_extract(BegDate, "[0-9]{1,2}$")) > 22 ~ "19",
                             T ~ "20")) %>%
  mutate(beginDate =  as.Date(paste0(str_extract(BegDate, "[0-9]{1,2}/[0-9]{1,2}/"),
                           century,
                           str_extract(BegDate, "[0-9]{1,2}$")), "%m/%d/%Y")) %>%
  mutate(endDate = as.Date(paste0(str_extract(EndDate, "[0-9]{1,2}/[0-9]{1,2}/"),
                           century,
                           str_extract(EndDate, "[0-9]{1,2}$")), , "%m/%d/%Y")) %>%
  mutate(year = as.integer(format(endDate, format="%Y"))) %>%
  mutate(RespPct = as.integer(RespPct)) %>%
  mutate(RespPct = replace_na(RespPct, 0))
```


```{r clean Gallup}
dfBigBusiness_clean = html_tbls[[5]] %>%
  slice(1:(n() - 2)) %>%
  filter(!row_number() == 2) %>% 
  mutate(X1 = case_when(X1 == "" ~ "year",
                        T ~ X1)) %>%
  janitor::row_to_names(1) %>%
  mutate(year = str_extract(year, "[0-9]{4}")) %>%
  mutate(across(where(is.character), as.integer)) %>%
  mutate(across(where(is.integer), ~replace_na(.x, 0))) 

```

## Prep for merge

```{r Roper merge}
dfRoper_m = dfRoper %>%
  mutate(AntitrustDirectionCombo = case_when(str_detect(AntitrustDirection, "pro") ~ "pro",
                                             str_detect(AntitrustDirection, "anti") ~ "anti",
                                             T ~ AntitrustDirection)) %>%
  group_by(QuestionTxt, AntitrustDirectionCombo, questionType, QuestionID) %>%
  summarise(RespPct = mean(RespPct), year = first(year), SampleSize = mean(SampleSize)) 
```

```{r Gallup merge}
dfBigBusiness_m = dfBigBusiness_clean %>%
  mutate(anti = `Great deal` + `Quite a lot`,
         ambig = Some + `No opinion`,
         pro = `Very little` + `None (vol.)`,
         QuestionID = paste("confidence in big business - Gallup", as.character(row_number()))) %>%
  select(year, anti:pro, QuestionID) %>%
  pivot_longer(!c(year, QuestionID),
               names_to = "AntitrustDirectionCombo",
               values_to = "RespPct") %>%
  mutate(questionType = "Gallup",
         QuestionTxt = "Now I am going to read you a list of institutions in American society. Please tell me how much confidence you, yourself, have in each one -- a great deal, quite a lot, some or very little? Big business")
```

## Analysis

```{r, include=FALSE}
dfRoper %>%
  filter(questionType == "overall") %>%
  select(RespPct, AntitrustDirection, year) %>%
  ggplot() + 
  geom_point(aes(x = year, y = RespPct, color = AntitrustDirection)) 

```

```{r, include=FALSE}
dfRoper_m %>%
  filter(questionType == "overall") %>%
  ggplot() + 
  geom_point(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_smooth(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) 



```

```{r, include=FALSE}
test = dfRoper %>%
  group_by(QuestionTxt) %>%
  summarise(first(QuestionTxt))

str_detect(test$QuestionTxt, "Do you think we need new laws to control big companies")
```

```{r, include=FALSE}

ggplot() + 
  geom_point(data = filter(dfRoper_m, questionType == "overall"), 
             aes(x = year, y = RespPct, color = AntitrustDirectionCombo))+
  geom_smooth(data = filter(dfRoper_m, questionType == "overall"), 
              aes(x = year, y = RespPct, color = AntitrustDirectionCombo))
```

```{r Gallup points, include=FALSE}
ggplot() + 
  geom_point(data = dfBigBusiness_m, aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_smooth(data = dfBigBusiness_m, aes(x = year, y = RespPct, color = AntitrustDirectionCombo))

```

```{r Roper + Gallup, include=FALSE}
ggplot() + 
  geom_point(data = filter(dfRoper_m, questionType == "overall"),
             aes(x = year, y = RespPct, color = AntitrustDirectionCombo))+
  geom_smooth(data = filter(dfRoper_m, questionType == "overall"),
              aes(x = year, y = RespPct, color = AntitrustDirectionCombo))+
  geom_point(data = dfBigBusiness_m, aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_smooth(data = dfBigBusiness_m, aes(x = year, y = RespPct, color = AntitrustDirectionCombo))



```

```{r, include=FALSE}
ggplot() + 
  geom_point(data =   filter(dfRoper_m, AntitrustDirectionCombo == "pro"),
             aes(x = year, y = RespPct))+
  geom_smooth(data =   filter(dfRoper_m, AntitrustDirectionCombo == "pro"),
              aes(x = year, y = RespPct))+
  geom_point(data = filter(dfBigBusiness_m, AntitrustDirectionCombo == "pro"),
             aes(x = year, y = RespPct)) +
  geom_smooth(data =  filter(dfBigBusiness_m, AntitrustDirectionCombo == "pro"),
              aes(x = year, y = RespPct))



```

```{r, include=FALSE}

dfRoper %>%
  mutate(RespPct = as.integer(RespPct)) %>%
  ggplot() + geom_point(aes(x = year, y = RespPct, color = AntitrustDirection))

```

```{r, include=FALSE}
dfRoper_m %>%
  filter(questionType == "overall") %>%
  pivot_wider(names_from = AntitrustDirectionCombo, values_from = RespPct) %>%
  mutate(proAntiRatio = pro/(anti + pro)) %>%
  ggplot() +
  geom_point(aes(x = year, y = proAntiRatio)) +
  geom_smooth(aes(x = year, y = proAntiRatio)) +
  geom_hline(yintercept = 0.5)
  
  # filter(AntitrustDirectionCombo != "ambig") %>%
  # group_by(QuestionTxt, year) %>%
  # summarise(RespPct = )
```

```{r, include=FALSE}
dfRoper_m %>%
  filter(questionType == "overall") %>%
  pivot_wider(names_from = AntitrustDirectionCombo, values_from = RespPct) %>%
  mutate(proAntiRatio = pro/(pro+ anti)) %>%
  ggplot() +
  geom_point(aes(x = year, y = proAntiRatio)) +
  geom_smooth(aes(x = year, y = proAntiRatio), 
              method = "loess") +
  theme_classic() +
  labs(x = "Year", y = "Proportion of pro-expansion opinions",
       title = "Proportion of public in favor of expanding antitrust enforcement",
       caption = "Source: Roper Center for Public Opinion Research")
```


### Linear regression 

```{r unweighted, include=FALSE}
lm_proShare = lm(data = filter(dfRoper_m, questionType == "overall" & AntitrustDirectionCombo == "pro"),
   RespPct ~ year)

summary(lm_proShare)
```


```{r, include=FALSE}


lmWeight = lm(data = filter(dfRoper_m, questionType == "overall" & AntitrustDirectionCombo == "pro" & year!=1999),
   RespPct ~ year, weights = SampleSize)

summary(lmWeight)

```
```{r, include=FALSE}
dfRoper_m %>%
  filter(questionType == "overall" & AntitrustDirectionCombo == "pro") %>%
  filter(year != 1999) %>%
  ggplot(aes(x = year, y = RespPct)) +
  geom_point(aes(x = year, y = RespPct)) +
  geom_smooth(method = "lm", mapping = aes(weight = SampleSize))

```

## Report

### Raw data
```{r}

ls_qs_df = bind_rows(dfRoper_m, (dfBigBusiness_m)) %>%
  ungroup() %>%
 # distinct(QuestionTxt, QuestionID, .keep_all = T) %>%
 # select(QuestionTxt, questionType) %>%
 # arrange(questionType) %>%
  mutate(questionType = case_when(questionType == "Gallup" ~ "Public confidence in big business (Gallup series)",
                                  questionType == "overall" ~ "Antitrust policy positions (Roper Center)",
                                  T ~ "Corporate influence in DC (Roper Center)")) 


# write.xlsx(filter(ls_qs_df, questionType == "Antitrust policy positions (Roper Center)"),
#            "ATEpoll_df.xlsx", 
#            sheetName = "Antitrust policy")
# write.xlsx(filter(ls_qs_df, questionType ==  "Public confidence in big business (Gallup series)"),
#            "ATEpoll_df.xlsx", 
#            sheetName = "Confidence in business",
#            append = T)
# write.xlsx(filter(ls_qs_df, questionType == "Corporate influence in DC (Roper Center)"),
#            "ATEpoll_df.xlsx", 
#            sheetName = "DC influence", 
#            append = T)

 

```



#### Df
```{r}

```


#### List of questions
```{r}

ls_qs_df = bind_rows(dfRoper_m, (dfBigBusiness_m)) %>%
  ungroup() %>%
  distinct(QuestionTxt, QuestionID, .keep_all = T) %>%
 # select(QuestionTxt, questionType) %>%
  arrange(questionType) %>%
  mutate(questionType = case_when(questionType == "Gallup" ~ "Public confidence in big business (Gallup series)",
                                  questionType == "overall" ~ "Antitrust policy positions (Roper Center)",
                                  T ~ "Corporate influence in DC (Roper Center)")) 

# 
# write.xlsx(filter(ls_qs_df, questionType == "Antitrust policy positions (Roper Center)"),
#            "List_polling_questions.xlsx", 
#            sheetName = "Antitrust policy")
# write.xlsx(filter(ls_qs_df, questionType ==  "Public confidence in big business (Gallup series)"),
#            "List_polling_questions.xlsx", 
#            sheetName = "Confidence in business",
#            append = T)
# write.xlsx(filter(ls_qs_df, questionType == "Corporate influence in DC (Roper Center)"),
#            "List_polling_questions.xlsx", 
#            sheetName = "DC influence", 
#            append = T)

 

```

##### Antitrust policy
```{r}
options(width = 60)
ls_qs_df$overall
```

##### Public confidence in big business (Gallup series)
```{r}
ls_qs_df$Gallup[[1]][1]
```


##### Corporate influence in DC
```{r}
ls_qs_df$powerDC
```



#### Roper Center - antitrust expansion
\
```{r}

dfRoper_m %>%
  filter(questionType == "overall" & AntitrustDirectionCombo != "ambig") %>%
  mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "pro" ~ "Pro",
                                             AntitrustDirectionCombo == "anti" ~ "Against",
                                             T ~ "Ambiguous")) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_point() +
  theme_classic() +
  scale_color_grey(start = 0, end = 0.5) + 
  labs(x = "Year", y = "% of survey respondents",
       color = "Position on expanding antitrust policy",
       title = "Public support for expanding antitrust policy", 
       caption = "Source: Roper Center for Public Opinion Research")+
  theme(legend.position = "bottom")
  
```


#### Gallup - confidence in big business
\
```{r}

dfBigBusiness_m %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
   mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "anti" ~ "High to moderate",
                                             AntitrustDirectionCombo == "pro" ~ "Little to none",
                                             T ~ "Ambiguous")) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_point() + 
  theme_classic() +
    scale_color_grey(start = 0, end = 0.5) + 
  labs(x = "Year", y = "% of survey respondents",
       color = "Level of confidence",
       title = "Public confidence in big business", 
       caption = "Source: Gallup- Confidence in Institutions")+
  theme(legend.position = "bottom")
  
```


#### Roper Center- power of business in DC
\
```{r}
dfRoper_m %>%
  filter(questionType == "powerDC") %>%
  mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "pro" ~ "Too much",
                                             AntitrustDirectionCombo == "anti" ~ "Too little",
                                             T ~ "No opinion")) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_point() + theme_classic()  + scale_color_grey(end = 0.6) + 
  labs(x = "Year", y = "% of survey respondents", 
       title = "Public opinion on big companies' level of power and influence in DC", 
       color = "Response",
       caption = "Source: Roper Center")


```


### Antitrust opinions over time
#### Graph

```{r}
dfRoper_m %>%
  filter(questionType == "overall") %>%
  pivot_wider(names_from = AntitrustDirectionCombo, values_from = RespPct) %>%
  mutate(proAntiRatio = pro/(pro+ anti)) %>%
  ggplot() +
  geom_point(aes(x = year, y = proAntiRatio)) +
  geom_smooth(aes(x = year, y = proAntiRatio), 
              method = "loess") +
  theme_classic() +
  labs(x = "Year", y = "Proportion of pro-expansion opinions",
       title = "Proportion of survey respondents in favor of expanding antitrust\nenforcement",
       caption = "Source: Roper Center for Public Opinion Research")

ggsave(path = fig.path, "proportion_pro_AE_loess.png")


```


#### Linear regression

```{r unweighted line}

dfRoper_lm = dfRoper_m %>%
  filter(questionType == "overall") %>%
  pivot_wider(names_from = AntitrustDirectionCombo, values_from = RespPct) %>%
  mutate(proportionPro = pro/(pro + anti)) 


lm_proShare = lm(data = dfRoper_lm,
   proportionPro ~ year)

summary(lm_proShare)
```

```{r}
dfRoper_m %>%
  filter(questionType == "overall") %>%
  pivot_wider(names_from = AntitrustDirectionCombo, values_from = RespPct) %>%
  mutate(proAntiRatio = pro/(pro+ anti)) %>%
  ggplot() +
  geom_point(aes(x = year, y = proAntiRatio)) +
  geom_smooth(aes(x = year, y = proAntiRatio), 
              method = "lm") +
  theme_classic() +
  labs(x = "Year", y = "Proportion of pro-expansion opinions",
       title = "Proportion of public in favor of expanding antitrust enforcement",
       caption = "Source: Roper Center for Public Opinion Research")

ggsave(path = fig.path, "proportion_pro_AE_lm.png")

```






### Confidence in big business as an insitution and the public's opinion about business's power

#### Confidence in big business
```{r}

dfBigBusiness_m %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
   mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "anti" ~ "High to moderate",
                                             AntitrustDirectionCombo == "pro" ~ "Little to none",
                                             T ~ "Ambiguous")) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_point() + theme_classic() + geom_smooth(method = "lm") +
    scale_color_grey(start = 0, end = 0.5) + 
  labs(x = "Year", y = "% of survey respondents",
       color = "Level of confidence",
       title = "Public confidence in big business", 
       caption = "Source: Gallup- Confidence in Institutions")+
  theme(legend.position = "bottom")


ggsave(path = fig.path, "public_confidence_business_lm.png")

  
```

```{r}
dfBigBusiness_m %>%
  filter(year == 1981 | year  == 1983)
```


```{r}

lm_proShareBigBusinessGallup = lm(data = filter(dfBigBusiness_m, AntitrustDirectionCombo == "anti"),
   RespPct ~ year)

summary(lm_proShareBigBusinessGallup)

```


```{r Gallup line}

dfBigBusiness_m %>%
     mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "anti" ~ "High to moderate",
                                             AntitrustDirectionCombo == "pro" ~ "Little to none",
                                             T ~ "No opinion or unclear")) %>%

ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) + 
  geom_point() + geom_smooth() + 
#  geom_point(data = dfBigBusiness_m, aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
 # geom_smooth(data = dfBigBusiness_m, aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
      scale_color_grey(start = 0, end = 0.5) + 
  labs(x = "Year", y = "% of survey respondents",
       color = "Level of confidence",
       title = "Public confidence in big business", 
       caption = "Source: Gallup- Confidence in Institutions")+
  theme(legend.position = "bottom") + theme_classic()
  

```
```{r}

dfBigBusiness_m %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
  group_by(year, AntitrustDirectionCombo) %>%
  summarise(RespPct = mean(RespPct), .groups = "keep") %>%
  pivot_wider(names_from = "AntitrustDirectionCombo", values_from = "RespPct") %>%
  mutate(proportion = (anti)/((pro) + (anti))) %>%
  ggplot(aes(x = year, y = proportion)) +
  geom_point() + theme_classic() + geom_smooth(method = "loess") +
    scale_color_grey(start = 0, end = 0.5) + 
  labs(x = "Year", y = "% of survey respondents",
       title = "Public confidence in big business",
       subtitle = "Proportion of survey respondents with high to moderate confidence in big business as a\n proportion of opininated respondents",
       caption = "Source: Gallup- Confidence in Institutions")
  
```


### Antitrust opinions, trust in business and business's power in DC
```{r}

dfRoper_m %>%
  filter(AntitrustDirectionCombo == "pro") %>%
  bind_rows(filter(mutate(dfBigBusiness_m, questionType = "Gallup"),
                   AntitrustDirectionCombo == "pro")) %>%
  mutate(questionType= case_when(questionType == "Gallup" ~ "Low to no confidence in big business",
                                 questionType == "overall" ~ "Pro expanding antitrust enforcement",
                                 T ~ "Big companies have too much power in DC")) %>%
  ggplot(aes(x = year, y = RespPct, color = questionType)) +
  geom_point() + geom_smooth() + theme_classic() +
  theme(legend.position = "bottom") +
  scale_color_grey(start = 0, end = 0.7) + 
  guides(color=guide_legend(nrow=2, byrow=F)) +
  labs(x = "Year", y = "% of survey respondents who responded affirmatively",
       title = "Public opinion on expanding antitrust enforcement, confidence\nin big business, and idea of power in DC",
      # subtitle = ",
      color = "Response",
      caption = "Source: Roper Center and Gallup- Confidence in Institutions")




```


```{r, include=F}

dfRoper_m %>%
  bind_rows(mutate(dfBigBusiness_m, questionType = "Gallup")) %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
  pivot_wider(names_from = "AntitrustDirectionCombo", 
              values_from = RespPct,
              values_fn = mean) %>%
  mutate(proportion = pro/(pro+anti)) %>%
  mutate(questionType = case_when(questionType == "Gallup" ~ "Confidence in big business",
                                  questionType == "overall" ~ "Antitrust policy",
                                  T~ "Big business' power in DC")) %>%
  ggplot(aes(x = year, y = proportion, color = questionType)) +
  geom_point() + geom_smooth() + theme_classic() +
  theme(legend.position = "bottom") + 
  scale_color_grey(start = 0, end = 0.7) + 
 # guides(color=guide_legend(nrow=2, byrow=F)) +
  labs(x = "Year", y = "% of survey respondents who responded affirmatively",
       title = "Proportion of public in favor of expanding antitrust enforcement, confidence\nin big business, and idea of power in DC",
      # subtitle = ",
      color = "",
      caption = "Source: Roper Center and Gallup- Confidence in Institutions")


ggsave(path = fig.path, "all_data.png")

```



```{r, include=F}

dfRoper_m %>%
  bind_rows(mutate(dfBigBusiness_m, questionType = "Gallup")) %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
  mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "pro" ~ "Pro-enforcement or \nanti-business",
                                             AntitrustDirectionCombo == "anti" ~ "Anti-enforcement or \npro-business",
                                             T ~ "Unclear or\nno opinion")) %>%
  mutate(questionType = case_when(questionType == "Gallup" ~ "Confidence in big business",
                                  questionType == "overall" ~ "Antitrust policy",
                                  T~ "Big business' power in DC")) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_point() + geom_smooth()+ facet_wrap(~questionType, scales = "free_x") +

    geom_point() + geom_smooth() + theme_classic() +
  theme(legend.position = "bottom") +
  scale_color_grey(end = 0.6) + 
  labs(x = "Year", y = "% of survey respondents",
       title = "Public opinion on antitrust policy and big business's influence",
      # subtitle = ",
      color = "Response",
      caption = "Source: Roper Center and Gallup- Confidence in Institutions")


ggsave(path = fig.path, "all_data_facet.png")


```


```{r, include=F}

dfRoper_m %>%
  bind_rows(mutate(dfBigBusiness_m, questionType = "Gallup")) %>%
  mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "pro" ~ "Pro-\nenforcement",
                                             AntitrustDirectionCombo == "anti" ~ "Anti-\nenforcement",
                                             T ~ "Unclear or\nno opinion")) %>%
  mutate(questionType = case_when(questionType == "Gallup" ~ "Confidence in big business",
                                  questionType == "overall" ~ "Antitrust policy",
                                  T~ "Big business' power in DC")) %>%
  ggplot(aes(x = year, y = RespPct)) +
  geom_point() + geom_smooth()+ facet_grid(AntitrustDirectionCombo ~ questionType) +
    geom_point() + geom_smooth() + theme_classic() +
  theme(legend.position = "bottom") +
  scale_color_grey() + 
  labs(x = "Year", y = "% of survey respondents",
       title = "Public opinion on expanding antitrust enforcement, confidence\nin big business, and idea of power in DC",
      # subtitle = ",
      color = "Type of question",
      caption = "Source: Roper Center and Gallup- Confidence in Institutions")




```

```{r, include=F}
dfRoper_m %>%
  filter(questionType == "powerDC" & AntitrustDirectionCombo != "ambig") %>%
  bind_rows(dfBigBusiness_m) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo)) +
  geom_point() + geom_smooth()
```

### Correlation analysis
```{r}

dfRoper_m %>%
  filter(questionType == "largeCompanyRegulation") %>%
  bind_rows(dfBigBusiness_m) %>%
  filter(year >= 1973 & year < 1983) %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
  mutate(questionType = ifelse(questionType == "Gallup", 
                               "Little to no confidence in big business",
                               "Supports greater goverment regulation of large companies"),
         AntitrustDirectionCombo = ifelse(AntitrustDirectionCombo == "pro",
                                          "Yes", "No")) %>%
  ggplot(aes(x = year, y = RespPct, color = AntitrustDirectionCombo,
             shape = questionType)) + geom_point() + geom_smooth(method = "lm") + 
  labs(x = "Year",
       y = "Respondent percentage",
       title = "Reponses to different questions",
       color = "Response",
       shape = "Polling question")


ggsave(path = fig.path, "correlation_fig.png")


```


```{r}


test = dfRoper_m %>%
  filter(questionType == "largeCompanyRegulation") %>%
  bind_rows(dfBigBusiness_m) %>%
    filter(year >= 1973 & year < 1983) %>%
  group_by(AntitrustDirectionCombo, year, questionType) %>%
  summarise(questionType = first(questionType),
            AntitrustDirectionCombo = first(AntitrustDirectionCombo),
            year = first(year),
            RespPct = mean(RespPct)) %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
  ungroup %>%
  select(questionType, AntitrustDirectionCombo, RespPct, year) %>%
 # arrange(year, AntitrustDirectionCombo) %>%
  pivot_wider(names_from = questionType,
              values_from = RespPct)


cor.test(test[test$AntitrustDirectionCombo == "pro",]$largeCompanyRegulation, 
         test[test$AntitrustDirectionCombo == "pro",]$Gallup)


cor.test(test[test$AntitrustDirectionCombo == "anti",]$largeCompanyRegulation, 
         test[test$AntitrustDirectionCombo == "anti",]$Gallup)

```

## Flourish figures
```{r fig 1}

bigBusinessTrust = dfBigBusiness_m %>%
  filter(AntitrustDirectionCombo != "ambig") %>%
   mutate(AntitrustDirectionCombo = case_when(AntitrustDirectionCombo == "anti" ~ "High to moderate",
                                             AntitrustDirectionCombo == "pro" ~ "Little to none",
                                             T ~ "Ambiguous")) %>%
  group_by(year, AntitrustDirectionCombo) %>%
  summarise(year = first(year), RespPct = mean(RespPct),
            AntitrustDirectionCombo = first(AntitrustDirectionCombo)) %>%
  ungroup()

setwd("data/final figures")
write.xlsx(bigBusinessTrust, "1_bigBusinessTrust.xlsx")
```


```{r fig 2: size and influence of major corp Gallup}
# Source: https://news.gallup.com/file/poll/188753/Satisfaction_with_Corporations_and_Regulations%20_160120.pdf; https://news.gallup.com/poll/188747/majority-americans-dissatisfied-corporate-influence.aspx

corpInfluence = data.frame(year = c(2001:2008, 2011:2016),
           total_satisfied = c(48, 50, 43, 38, 38, 35, 39, 35, 29, 30, 35, 35, 36, 35),
           total_dissatisfied = c(48, 47, 54, 61, 59, 62, 58, 61, 67, 64, 61, 63, 59, 63)
)


setwd("data/final figures")
write.xlsx(corpInfluence, "2_corpInfluence.xlsx")
```




```{r fig 3 roper polls}
roperPolls = dfRoper_m %>%
  filter(questionType == "overall") %>%
  pivot_wider(names_from = AntitrustDirectionCombo, values_from = RespPct) %>%
  mutate(proAntiRatio = pro/(pro+ anti)) %>%
  select(year, proAntiRatio)%>%
  ungroup()

setwd("data/final figures")
write.xlsx(roperPolls, "3_roperPolls.xlsx")

```


