---
title: "Antitrust enforcement"
author: "Sima Biondi"
date: "5/3/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(tidyr)
library(finalfit)


```

#Set up
```{r}
setwd("~/Desktop/Posner/antitrust") 
getwd()
```
# First draft of position changes
## Load Table 1
```{r}
df_diffs_profs= read.csv("diff_positions_comp.csv")
head(df_diffs_profs)
df_diffs_profs_1 =  df_diffs_profs %>% 
  gather(time_period, diff,  Diff_pre_76:Diff_post_75)
head(df_diffs_profs_1)
```

### Difference graph including both time periods
```{r}
p1 = ggplot(data=df_diffs_profs_1, aes(x=top, y= diff, fill = time_period)) +
  geom_bar(stat="identity", position=position_dodge()) + 
  xlab("Type of position") + ylab("Difference (%) in number of officials employed") + 
  ggtitle("Difference in compositions of high-ranking antitrust officials") + 
  scale_fill_discrete(name="Time period", labels= c("Post-1975", "Pre-1976"))

pdf("diff_graph_FL.pdf")
print(p1)
dev.off()
```

# Second draft of position changes

## Load whole data set
```{r} 
#move the data set so if you want to run again change the working directory
df = read.csv("Old versions of data/Part_2_v1.csv")
head(df)
```

## Create datasets of previous positions: remove unnecessary vars, split into 2 separate dfs 
```{r}
df_alt_pre76_prev = data.frame(Type_of_prev_position = "Alternate", n = 4)
df_pre76_previous = df %>%
  select(Year_started, Type_of_prev_position, Type_of_following_position) %>%
  filter(Year_started < 1976) %>%
  count(Type_of_prev_position) %>%
  filter(n >3 | Type_of_prev_position == "Academia") %>%
  bind_rows(df_alt_pre76_prev) %>%
  mutate(percent = n/sum(df_pre76_previous$n), time_period = "pre_76")

df_alt_post75_prev = data.frame(Type_of_prev_position = "Alternate", n = 2)
df_post75_prev = df %>%
  select(Year_started, Type_of_prev_position, Type_of_following_position) %>%
  filter(Year_started > 1975) %>%
  count(Type_of_prev_position) %>%
  filter(n > 2 | Type_of_prev_position == "Private practice") %>%
  bind_rows(df_alt_post75_prev) %>%
  mutate(percent = n/sum(df_post75_prev$n), time_period = "post_75")

prev_position_df = rbind(df_pre76_previous, df_post75_prev)

```


## Create datasets of future positions: remove unnecessary vars, split into 2 separate dfs 
```{r}
df_alt_pre76_future = data.frame(Type_of_following_position = "Alternate", n = 22)
df_pre76_future = df %>%
  select(Year_started, Type_of_prev_position, Type_of_following_position) %>%
  filter(Year_started < 1976) %>%
  count(Type_of_following_position) %>%
  filter(Type_of_following_position == "Academia" | Type_of_following_position == "Government" | Type_of_following_position == "Industry" | Type_of_following_position == "Law firm" | Type_of_following_position == "Private practice") %>%
  bind_rows(df_alt_pre76_future) %>%
  mutate(percent = n/sum(df_pre76_future$n), time_period = "pre_76")

df_alt_post75_future = data.frame(Type_of_following_position = c("Private practice", "Alternate"), n = c(0,9))
df_post75_future = df %>%
  select(Year_started, Type_of_prev_position, Type_of_following_position) %>%
  filter(Year_started > 1975) %>%
  count(Type_of_following_position) %>%
  filter(Type_of_following_position == "Academia" | Type_of_following_position == "Government" | Type_of_following_position == "Industry" | Type_of_following_position == "Law firm") %>%
  bind_rows(df_alt_post75_future) %>%
  mutate(percent = n/sum(df_post75_future$n), time_period = "post_75")

future_position_df = rbind(df_pre76_future, df_post75_future)

```


## Create graphs
```{r}

p_previous_positions = ggplot(data = prev_position_df, aes(x =Type_of_prev_position, y= percent, fill = time_period)) + geom_bar(stat="identity", position=position_dodge()) +
  xlab("Type of position") + ylab("% of officials employed") +   
  ggtitle("Composition of primary position before joining") + 
  scale_fill_discrete(name="Time period", labels= c("Post-1975", "Pre-1976"))

p_future_positions = ggplot(data = future_position_df, aes(x = Type_of_following_position, y= percent, fill = time_period)) + geom_bar(stat="identity", position=position_dodge()) +
  xlab("Type of position") + ylab("% of officials employed") +   
  ggtitle("Composition of primary position after leaving") + 
  scale_fill_discrete(name="Time period", labels= c("Post-1975", "Pre-1976"))


```

## Creating 1 image of previous and future employment
```{r}


 
pdf("diff_graph_FL_v2.pdf")
print(p_previous_positions)
print(p_future_positions)
dev.off()


```





# Summary statistics - 
## What I want to do:
### 1. Create new variables: length_of_tenure 
### 2. Distributions of key variables: 
####    Administration_appointee, party_affiliation, Education, Type of previous position, 
####    generalized_previous_experience (turn into 5 categorical variables?),
####    Following_position, generalized_following_exp, appointment_age
### 3. Check for missing data

## Load and clean data
```{r}
df = read.csv("Part_2_v3.csv")
df[is.na(df)] = 0
df = df %>%
  select(-Source, -Source2, -Source3, -Notes, -Appointment_age, -Appointment_age_rounded) #remove cols
head(df)

```

## Create new variable: time_period, length of tenure, appointment age
```{r}
df = df %>%
  mutate(time_period = ifelse(Year_started < 1976, "pre", "post")) %>%
  mutate(length_of_tenure = ifelse(Year_ended-Year_started > 0, Year_ended-Year_started, NA)) %>%
  mutate(age_at_appoint = ifelse(Year_started-Birth_year < 100, Year_started-Birth_year, NA)) #removing unknown DOBs from calc
```


## Summary statistics
```{r}
summary(select(df, -First_name, -Middle_name, -Last_name, -Suffix, -FTC_seat, -Education, -Previous_position,
               -Generalized_previous_experience, -Following_position, -Generalized_following_experience))
```

## Summary graphics (Year started, Year ended, admin appointee, party affiliation)
```{r}

#Year started
ggplot(df, aes(x=Year_started)) + geom_histogram(binwidth = 10)

#Year ended
ggplot(df, aes(x=Year_ended)) + geom_histogram(binwidth = 10)

#Administration appointee
table(df$Administration_appointee)

#Party_affiliation
table(df$Party_affiliation)
table(subset(df, Year_started < 1976)$Party_affiliation)
table(subset(df, Year_started > 1975)$Party_affiliation)
prop.table(table(df$Party_affiliation))

```
## Summary graphics continued: education, previous, following employment
```{r}


#Education

df_sum_edu = df %>%
  select(starts_with("Education")) %>%
  select(-Education) %>%
  summarise_all(list(mean = "mean")) %>%
  pivot_longer(cols = starts_with("Education"))

ggplot(df_sum_edu, aes(x = value, color = name, fill = name)) + geom_histogram(alpha=0.6, binwidth = 5)

t1 = table(df$Education_law, df$Education_LLB, df$Education_JD)
ftable(t1)

 as.data.frame(prop.table(table(df$time_period, df$Education_law)))


count(df, 'Education_law', 'Education_JD')

ggplot(a, aes(x=Var1, y = Freq)) + geom_bar(stat = "identity")



ls(df)
head(df)
```



## Summary graphics continued: age, length of tenure, law firms mentioned
```{r}
# Age
ggplot(df, aes(x = age_at_appoint)) + geom_histogram(binwidth = 10) + geom_vline(aes(xintercept = mean(age_at_appoint, na.rm = T)), 
  color = "red")
ggplot(df[df$Year_started < 1976,], aes(x = age_at_appoint)) + geom_histogram(binwidth = 10) + geom_vline(aes(xintercept = mean(age_at_appoint, na.rm = T)), 
  color = "blue")
ggplot(df[df$Year_started >1975,], aes(x = age_at_appoint)) + geom_histogram(binwidth = 10) + geom_vline(aes(xintercept = mean(age_at_appoint, na.rm = T)), 
  color = "green")

mean(subset(df, Year_started < 1976)$age_at_appoint*1, na.rm = T) #might want to consider adjusting for shorter lifespans prior to 70s
mean(subset(df, Year_started > 1975)$age_at_appoint, na.rm = T)

#Length of tenure
ggplot(df, aes(x = length_of_tenure)) + geom_histogram(binwidth = 5)
ggplot(df[df$Year_started < 1976,], aes(x = length_of_tenure)) + geom_histogram(binwidth = 5) + geom_vline(aes(xintercept = mean(length_of_tenure, na.rm = T)), color = "blue")
ggplot(df[df$Year_started > 1975,], aes(x = length_of_tenure)) + geom_histogram(binwidth = 5) + geom_vline(aes(xintercept = mean(length_of_tenure, na.rm = T)), color = "green")

#Law firms mentioned
table(df$Following_law_firms)
```


## Missing data
```{r}
df %>% missing_plot()
```



## Future ideas
```{r}
table(df$Party_affiliation, df$length_of_tenure)
```

