---
title: "Analysis of previous/following position of AAGs and FTC Commissioners"
author: "Sima Biondi"
date: "9/13/2021"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setupNoms, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      warning = F, message = F)
options(warn = -1)
library(ggplot2)
library(dplyr)
library(tidyr)
library(finalfit)
library(readxl)
library(writexl)
library(forcats)
library(stringr)
library(kableExtra)
library(lemon)
library(flextable)
library(usethis)
fig.path = here::here("figs/final draft")

```

```{r}
#git_sitrep()
#gitcreds::gitcreds_set()
```


## Merging nomination data with personnel Excel
```{r}
nomination_df = read_excel("data/Summary of Nominations - completed.xlsx") %>%
  slice_head(n = 137) %>%
  mutate(renominationsAfter68 = case_when(Last_name == "Azcuenaga" |
                                           Last_name == "Dixon" ~ T,
                                         T ~ F)) %>%
  mutate(multipleNoms = case_when(Last_name == "James" |
                                    Last_name == "Varney" |
                                            Last_name == "Pitofsky" ~ T,
                                          T ~ F)) %>%
  select(First_name: Last_name, hearingDocsObtained: Year_ended, multipleNoms) 

part2_df = read_excel("data/Part_2_for_merge.xlsx") 

part2_df_with_noms = part2_df %>%
  select(-hearingDocsObtained, -Year_started, -Year_ended) %>%
  filter(!Last_name %in% c("James", "Varney", "Pitofsky")) %>%
  right_join(filter(nomination_df, !Last_name %in% c("James", "Varney", "Pitofsky")),
             by = c("First_name", "Middle_name", "Last_name")) %>%
  bind_rows(left_join(filter(nomination_df, Last_name %in% c("James", "Varney", "Pitofsky")),
          filter(part2_df, Last_name %in% c("James", "Varney", "Pitofsky")))) %>%
  mutate(Administration_appointee = case_when(Last_name == "Dixon" & Year_started == 1974 ~ "Ford",
                                              Last_name == "Azcuenaga" & Year_started == 1991 ~ "GHWB",
                                              T ~ Administration_appointee)) %>%
  select(!starts_with("Education_") &
         !starts_with("Prev_exp") &
         !starts_with("Follow_exp_") &
         -Appointment_age)
  

# part2_df_with_noms %>%
  # write_xlsx("data/personnel_data_220406.xlsx")
  


```


## Identifying renominated individuals
```{r}
library(rvest)

page = read_html("https://en.wikipedia.org/wiki/List_of_members_of_the_Federal_Trade_Commission")

html_tbls = page %>% 
  html_elements("table") %>% 
  html_table()
 
time_in_office = html_tbls[[2]] %>%
  rowwise() %>%
  mutate(startYear = as.integer(str_extract_all(`Years in office`, ("[0-9]{4}"))[[1]][1])) %>%
  mutate(endYear = as.integer(str_extract_all(`Years in office`, ("[0-9]{4}"))[[1]][2])) %>%
  mutate(diffMoreSeven = ifelse(endYear - startYear > 7, T, F)) %>%
  filter(diffMoreSeven) 
```


## Updating dataframe with new data
```{r}
df = part2_df_with_noms 
```

## Data reshaping and calculations
### Previous positions
```{r}
prev_position_df = df %>%
  mutate(era = ifelse(Year_started < 1976, "pre-76", "post-75")) %>%
  group_by(Type_of_previous_position, era) %>%
  count() %>%
  ungroup() %>%
  group_by(Type_of_previous_position) %>%
  mutate(percent_by_position = n/sum(n)) %>%
  ungroup() %>%
  group_by(era) %>%
  mutate(percent_by_era = n/sum(n))



```

### Following positions
```{r}
following_positions_df =  df %>%
  mutate(era = ifelse(Year_started < 1976, "pre-76", "post-75")) %>%
  group_by(Type_of_following_position, era) %>%
  count() %>%
  ungroup() %>%
  group_by(Type_of_following_position) %>%
  mutate(percent_by_position = n/sum(n)) %>%
  ungroup() %>%
  group_by(era) %>%
  mutate(percent_by_era = n/sum(n))
```


### Summarizing revolving door
```{r}

df_summary_long = df %>%
  mutate(era = case_when(Year_started < 1976 ~ "Pre-1976",
                         T ~ "Post-1975")) %>%
  select(Type_of_previous_position, Type_of_following_position, era) %>%
  mutate(sum_type_prev_pos = case_when(
    Type_of_previous_position == "Industry" | Type_of_previous_position == "Law firm" ~ "Law firm &\nindustry",
    Type_of_previous_position == "Government" | 
      Type_of_previous_position == "Alternate" |
      Type_of_previous_position == "Academia" ~ "Government &\nacademia",
    T ~ "Other")) %>%
  mutate(sum_type_follow_pos = case_when(
    Type_of_following_position == "Industry" | 
      Type_of_following_position == "Law firm" ~ "Law firm &\nindustry",
    Type_of_following_position == "Government" | 
      Type_of_following_position == "Alternate" |
      Type_of_following_position == "Academia" ~ "Government &\nacademia",
    T ~ "Other")) %>%
  pivot_longer(cols = !era, values_to = "Type of positions") %>%
  filter(name != "Type_of_previous_position" & name != "Type_of_following_position") %>%
  mutate(direction = case_when(str_detect(name, "prev") ~ "Previous position",
                               T ~ "Following position")) %>%
  mutate(direction_f = factor(direction, levels = c('Previous position', 'Following position')),
         Era = factor(era, levels = c('Pre-1976', 'Post-1975'))) 


```

```{r}

df_summary = df_summary_long %>%
  group_by(era, name, `Type of positions`, direction) %>%
  summarise(count = n()) %>%
  ungroup() %>%
  group_by(era, direction) %>%
  mutate(freq = (count/sum(count))* 100) %>%
  mutate(direction = case_when(str_detect(name, "prev") ~ "Previous position",
                               T ~ "Following position")) %>%
  mutate(direction_f = factor(direction, levels = c('Previous position', 'Following position')),
         Era = factor(era, levels = c('Pre-1976', 'Post-1975'))) 

```




## Create figures
```{r}

#cbbPalette = c("#000000", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

p_previous_positions = df_summary %>%
  filter(direction == "Previous position") %>%
  ggplot(aes(x = `Type of positions`, y= freq, fill = Era)) +
  geom_col(position = position_dodge2(reverse = F)) +
  labs(x = "Type of position",
       y = "% of officials employed",
       title = "Composition of primary position before joining") + 
  scale_fill_hue(name="Time period", labels= c("Pre-1976", "Post-1975")) +
  theme_classic() + scale_fill_grey()


p_future_positions = df_summary %>%
  filter(direction == "Following position") %>%
  ggplot(aes(x = `Type of positions`, y= freq, fill = Era)) + 
  geom_col(stat="identity", position=position_dodge2()) +
  labs(x = "Type of position", y = "% of officials employed",
       title = "Composition of primary position after leaving") + 
  scale_fill_discrete(name="Era", labels= c("Pre-1976", "Post-1975")) +
  theme_classic()   +scale_fill_grey()


p_summary_graph = df_summary %>%
  filter(`Type of positions` != "Other") %>%
  ggplot(aes(x = `Type of positions`)) + 
  geom_col(aes(y = freq, fill = Era),
           position = position_dodge2()) +
  facet_wrap(vars(direction_f), scales = "free", dir = "v") +
    labs(title = "Composition of officials' career trajectories", y = "% of officials employed") +
  scale_fill_grey() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "bottom",
        panel.background = element_rect(fill = "white"))  +
  expand_limits(y = 100)



p_summary_graph_labels = df_summary %>%
  filter(`Type of positions` != "Other") %>%
  ggplot(aes(x = Era, y = freq, fill = Era)) + 
  geom_col(position = position_dodge2()) + 
  facet_grid(vars(direction_f),  vars(`Type of positions`), 
            scales = "free_x"
            ) +
  labs(title = "Composition of officials' career trajectories", y = "% of officials employed") +
  scale_fill_grey() +
  theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        axis.ticks.x = element_blank(), 
        axis.text.x=element_blank(), 
        axis.title.x = element_blank(),
        legend.position = "bottom",
        panel.background = element_rect(fill = "white")) 

```

```{r fig.height=8, fig.asp=0.8}

p_summary_graph
ggsave(path = fig.path, "official_career_trajectories.png")

```



```{r}

#p_previous_positions
#ggsave(path = fig.path, "previous_position_fig.png")

#p_future_positions
#ggsave(path = fig.path, "future_position_fig.png")

#p_summary_graph
#ggsave(path = fig.path, "summary_position_fig.png")


#p_summary_graph_labels
#ggsave(path = fig.path, "summary_position_grid_fig.png")

```


```{r party affiliation}

df_party_affil = read_excel("data/Part_2_ftc_bios_presidents.xlsx")
df_party_affil_tbl =  df_party_affil %>%
  mutate(partyMatchBool = case_when(presidentParty == partyAffiliation ~ "match",
                                 T ~ "no match")) %>%
  mutate(partyMatchString = case_when(presidentParty == "D" & partyAffiliation == "D" ~ "D",
                                      presidentParty == "D" & partyAffiliation == "Progressive" ~ "D",
                                      presidentParty == "R" & partyAffiliation == "R" ~ "R",
                                      presidentParty == "D" & partyAffiliation == "R" ~ "Dem-leaning Rep",
                                      presidentParty == "R" & partyAffiliation == "D" ~ "Rep-leaning Dem",
                                      partyAffiliation == "NA" ~ "No individual affiliation",
                                      partyAffiliation == "Independent" ~ "Independent",

                                 T ~ "no match")) %>%
  group_by(partyMatchString) %>%
  count() %>%
  kable()


df_party_affil_fig_dot = df_party_affil %>%
 # filter(presidentParty == "acting") %>%
  ggplot(aes(x = Year_started, fill = presidentParty)) + geom_dotplot(binwidth=4, method='histodot')    


# df_party_affil %>%
#  # filter(presidentParty == "acting") %>%
#   ggplot(aes(x = Year_started, fill = presidentParty)) + geom_dotplot(method='histodot', binwidth = 1)    


df_party_affil_fig_bar = df_party_affil %>%
  ggplot(aes(x = Year_started, fill = presidentParty)) + 
    geom_histogram(binwidth = 8, position = "dodge") + 
  theme_classic() +
  scale_fill_manual(values = c("acting" = "green",
                               "D" = "blue",
                               "R" = "red")) +
  labs(x = "Year", y = "Count of officials", fill = "Party of nominating president",
       title = "Party of nominating president for antitrust AAGs and FTC Commissioners")
 




```


## Nomination analysis

### Clean
```{r clean nomination data}

#table(part2_df_with_noms$hearingDocsObtained)

nomination_df_clean = part2_df_with_noms %>%
  filter(str_detect(hearingDocsObtained, "[Yy]es") |
           str_detect(hearingDocsObtained, "No - Recess appointment") |
           str_detect(hearingDocsObtained, "No Committee hearing") |
           str_detect(hearingDocsObtained, "Only have the documents, not the hearing itself.")) %>%
  mutate(enforcementEra = ifelse(Year_started < 1975, "High enforcement", "Low enforcement")) %>%
  mutate(era = case_when(Year_started > 1968 & Year_started < 1980 ~ "1969-1979",
                         Year_started > 1979 & Year_started < 1990 ~ "1980-1989",
                         Year_started > 1989 & Year_started < 2000 ~ "1990-1999",
                         Year_started > 1999 & Year_started < 2010 ~ "2000-2009",
                         Year_started > 2009 & Year_started < 2020 ~ "2010-",
                         T ~ as.character(NA))) %>%
  mutate(hearingMinutesInt = as.double(`Hearing duration (in minutes)`)) %>%
  mutate(substantiveDiscussionsYes = ifelse(str_detect(`Substantive discussions`, "[Yy]es"), 
                                         1, 0)) %>%
  mutate(substantiveDiscussionsNo = ifelse(str_detect(`Substantive discussions`, "[Yy]es"), 
                                              0, 1)) %>%
  mutate(proEnforcementYes = ifelse(str_detect(`Pro-Enforcement`, "Yes") &
                                    substantiveDiscussionsYes == 1, 1, 0)) %>%
  mutate(proEnforcementNo = ifelse(str_detect(`Pro-Enforcement`, "No") &
                                     substantiveDiscussionsYes == 1, 1, 0)) %>%
  mutate(proEnforcementMixed = ifelse(str_detect(`Pro-Enforcement`, "Mixed") & 
                                        substantiveDiscussionsYes == 1, 1, 0)) 


```




```{r}
library(rvest)

page = read_html("https://en.wikipedia.org/wiki/List_of_presidents_of_the_United_States")

html_tbls = page %>%
  html_elements("table") %>%
  html_table()

presidentialTermStartYears = html_tbls[[2]] %>%
  select(`Name(Birth–Death)`, Term) %>%
  rowwise() %>%
  mutate(termStartYear = as.integer(str_extract_all(Term, ("[0-9]{4}"))[[1]][1])) %>%
  mutate(Name = case_when(str_detect(`Name(Birth–Death)`, "\\[") ~ 
                            str_extract(`Name(Birth–Death)`, "\\s[A-z][a-z]+\\["),
                          T ~ str_extract(`Name(Birth–Death)`, "\\s[A-z][a-z]+\\("))) %>%
  mutate(Name = str_sub(Name, 2, nchar(Name)-1)) %>%
  filter(termStartYear > 1932) %>%
  group_by(Name, termStartYear) %>%
  summarize(Name = first(Name), 
            termStartYear = first(termStartYear)) %>%
  ungroup() %>%
  mutate(Name = case_when(Name == "Roosevelt" ~ "FDR",
                          Name == "Kennedy" ~ "JFK",
                          Name == "Johnson" ~ "LBJ",
                          Name == "Bush" & termStartYear == 1989 ~ "GHWB",
                          Name == "Bush" & termStartYear == 2001 ~ "GWB",
                          T ~ Name))

```


### Nomination data split by president
```{r}

noms_by_pres_tbl = nomination_df_clean %>%
  left_join(presidentialTermStartYears, 
            by = c( "Administration_appointee" = "Name")) %>%
  filter(Year_started > 1968) %>%
  group_by(Administration_appointee) %>%
  summarise(Count = n(),
            Mean = round(mean(hearingMinutesInt, na.rm = T), 1),
            Median = median(hearingMinutesInt, na.rm = T),
            across(substantiveDiscussionsYes, ~(sum(., na.rm = T))),
            across(substantiveDiscussionsNo, ~(sum(., na.rm = T))),
            across(proEnforcementYes, ~(sum(., na.rm = T))),
            across(proEnforcementNo, ~(sum(., na.rm = T))),
            across(proEnforcementMixed, ~(sum(., na.rm = T)))) %>%
  ungroup() %>%
  mutate(percentSubstantive = 
           substantiveDiscussionsYes / (substantiveDiscussionsYes +
                                        substantiveDiscussionsNo)) %>%
  mutate(percentSubstantive = (100*round(percentSubstantive, 4))) %>%
  select(Administration_appointee: substantiveDiscussionsNo, 
         percentSubstantive,
         proEnforcementYes:proEnforcementMixed) %>%
  left_join(presidentialTermStartYears, 
            by = c( "Administration_appointee" = "Name")) %>%
  arrange(termStartYear) %>%
  rename(` ` = Administration_appointee,
         Yes = substantiveDiscussionsYes,
         No = substantiveDiscussionsNo,
         `%` = percentSubstantive,
         Pro = proEnforcementYes,
         Anti = proEnforcementNo,
         Mixed = proEnforcementMixed) %>%
  select(-termStartYear) #%>%
 #  kable(caption = "Nomination hearing data by president",
 #        booktabs = T, linesep = "", longtable = T, "html", label = "test") %>%
 #  kable_styling(full_width = T
 #    #latex_options  = c("striped")
 #    ) %>%
 #  add_header_above(c(" " = 2, "Duration of nomination \nhearings (in minutes)" = 2, 
 #                     "Substantive antitrust\n discussions?" = 3, 
 #                     "Substantive attitudes\ntoward enforcement" = 3))
 # # kable_paper(html_font = "times")



```

### Nomination data split by type of position and president
```{r}

noms_by_pres_and_pos = nomination_df_clean %>%
  left_join(presidentialTermStartYears, 
            by = c( "Administration_appointee" = "Name")) %>%
  filter(Year_started > 1968) %>%
  group_by(Administration_appointee, Employer) %>%
  summarise(Count = n(),
            Mean = round(mean(hearingMinutesInt, na.rm = T), 1),
            Median = median(hearingMinutesInt, na.rm = T),
            across(substantiveDiscussionsYes, ~(sum(., na.rm = T))),
            across(substantiveDiscussionsNo, ~(sum(., na.rm = T))),
            across(proEnforcementYes, ~(sum(., na.rm = T))),
            across(proEnforcementNo, ~(sum(., na.rm = T))),
            across(proEnforcementMixed, ~(sum(., na.rm = T)))) %>%
  ungroup() %>%
  mutate(percentSubstantive = 
           substantiveDiscussionsYes / (substantiveDiscussionsYes + substantiveDiscussionsNo)) %>%
  mutate(percentSubstantive = 100*round(percentSubstantive, 4)) %>%
  select(Administration_appointee: substantiveDiscussionsNo, 
         percentSubstantive,
         proEnforcementYes:proEnforcementMixed) %>%
  left_join(presidentialTermStartYears, 
            by = c( "Administration_appointee" = "Name")) %>%
  arrange(termStartYear) %>%
  rename(` ` = Administration_appointee,
         Agency = Employer,
         Yes = substantiveDiscussionsYes,
         No = substantiveDiscussionsNo,
         `%` = percentSubstantive,
         Pro = proEnforcementYes,
         Anti = proEnforcementNo,
         Mixed = proEnforcementMixed) %>%
  select(-termStartYear) # %>%
  # kable(caption = "Nomination hearing data by president and agency",
  #       booktabs = T, linesep = "", longtable = T, "html") %>%
  # kable_styling(latex_options  = c("striped")) %>%
  # add_header_above(c(" " = 3, "Duration of nomination \nhearings (in minutes)" = 2, 
  #                    "Substantive antitrust\n discussions?" = 3, 
  #                    "Substantive attitudes\ntoward enforcement" = 3))


```

### Nomination data split by type of position
```{r}

noms_by_position = nomination_df_clean %>%
  filter(Year_started > 1968) %>%
  group_by(Employer) %>%
  summarise(Count = n(),
            Mean = round(mean(hearingMinutesInt, na.rm = T), 1),
            Median = median(hearingMinutesInt, na.rm = T),
            across(substantiveDiscussionsYes, ~(sum(., na.rm = T))),
            across(substantiveDiscussionsNo, ~(sum(., na.rm = T))),
            across(proEnforcementYes, ~(sum(., na.rm = T))),
            across(proEnforcementNo, ~(sum(., na.rm = T))),
            across(proEnforcementMixed, ~(sum(., na.rm = T)))) %>%
  ungroup() %>%
  mutate(percentSubstantive = 
           substantiveDiscussionsYes / (substantiveDiscussionsYes + substantiveDiscussionsNo)) %>%
  mutate(percentSubstantive = 100*round(percentSubstantive, 4)) %>%
  select(Employer: substantiveDiscussionsNo, 
         percentSubstantive,
         proEnforcementYes:proEnforcementMixed) %>%
  rename(Agency = Employer,
         Yes = substantiveDiscussionsYes,
         No = substantiveDiscussionsNo,
         `%` = percentSubstantive,
         Pro = proEnforcementYes,
         Anti = proEnforcementNo,
         Mixed = proEnforcementMixed)# %>%
  # kable(caption = "Nomination hearing data by decade",
  #       booktabs = T, linesep = "", longtable = T) %>%
  # kable_styling(latex_options  = c("striped")) %>%
  # add_header_above(c(" " = 2, "Duration of nomination \nhearings (in minutes)" = 2, 
  #                    "Substantive antitrust\n discussions?" = 3, 
  #                    "Substantive attitudes\ntoward enforcement" = 3))

```


### Nomination data split by decade
```{r}
noms_by_decade = nomination_df_clean %>%
  group_by(era) %>%
  summarise(Count = n(),
            Mean = round(mean(hearingMinutesInt, na.rm = T), 1),
            Median = median(hearingMinutesInt, na.rm = T),
            across(substantiveDiscussionsYes, ~(sum(., na.rm = T))),
            across(substantiveDiscussionsNo, ~(sum(., na.rm = T))),
            across(proEnforcementYes, ~(sum(., na.rm = T))),
            across(proEnforcementNo, ~(sum(., na.rm = T))),
            across(proEnforcementMixed, ~(sum(., na.rm = T)))) %>%
  ungroup() %>%
  mutate(percentSubstantive = 
           substantiveDiscussionsYes / (substantiveDiscussionsYes + substantiveDiscussionsNo)) %>%
  mutate(percentSubstantive = 100*round(percentSubstantive, 4)) %>%
  filter(!is.na(era)) %>%
  select(era: substantiveDiscussionsNo, 
         percentSubstantive,
         proEnforcementYes:proEnforcementMixed) %>%
  rename(` ` = era,
         Yes = substantiveDiscussionsYes,
         No = substantiveDiscussionsNo,
         `%` = percentSubstantive,
         Pro = proEnforcementYes,
         Anti = proEnforcementNo,
         Mixed = proEnforcementMixed) #%>%
  # kable(caption = "Nomination hearing data by decade",
  #       booktabs = T, linesep = "", longtable = T, "html") %>%
  # kable_styling(latex_options  = c("striped")) %>%
  # add_header_above(c(" " = 2, "Duration of nomination \nhearings (in minutes)" = 2, 
  #                    "Substantive antitrust\n discussions?" = 3, 
  #                    "Substantive attitudes\ntoward enforcement" = 3))

# nomination_df_clean %>%
#   arrange(Year_started) %>%
#   filter(era == "2000-2009") %>%
#   select(Last_name, Year_started, `Substantive discussions`) 


## edith and judith??
## no substantive dicussions variable entry for Varney 2009?


```

### Nomination data split by party in control of Senate
```{r}

noms_by_partyControl = nomination_df_clean %>%
  group_by(senateControlParty) %>%
  mutate(senateControlParty = recode(senateControlParty, 
                                     "D" = "Democrats",
                                     "R" = "Republicans")) %>%
  summarise(Count = n(),
            Mean = round(mean(hearingMinutesInt, na.rm = T), 1),
            Median = median(hearingMinutesInt, na.rm = T),
            across(substantiveDiscussionsYes, ~(sum(., na.rm = T))),
            across(substantiveDiscussionsNo, ~(sum(., na.rm = T))),
            across(proEnforcementYes, ~(sum(., na.rm = T))),
            across(proEnforcementNo, ~(sum(., na.rm = T))),
            across(proEnforcementMixed, ~(sum(., na.rm = T)))) %>%
  ungroup() %>%
  mutate(percentSubstantive = 
           substantiveDiscussionsYes / (substantiveDiscussionsYes + substantiveDiscussionsNo)) %>%
  mutate(percentSubstantive = 100*round(percentSubstantive, 4)) %>%
  filter(!is.na(senateControlParty)) %>%
  select(senateControlParty: substantiveDiscussionsNo, 
         percentSubstantive,
         proEnforcementYes:proEnforcementMixed) %>%
  rename(`Senate control` = senateControlParty,
         Yes = substantiveDiscussionsYes,
         No = substantiveDiscussionsNo,
         `%` = percentSubstantive,
         Pro = proEnforcementYes,
         Anti = proEnforcementNo,
         Mixed = proEnforcementMixed) #%>%
  # kable(caption = "Nomination hearing data by majority party in Senate",
  #       booktabs = T, linesep = "", longtable = T, "html") %>%
  # kable_styling(full_width = T 
  #   #latex_options = c("striped")
  #   ) %>%
  # add_header_above(c(" " = 2, "Duration of nomination \nhearings (in minutes)" = 2, 
  #                    "Substantive antitrust\n discussions?" = 3, 
  #                    "Substantive attitudes\ntoward enforcement" = 3))


```



### Nomination data split by era and party in control of Senate
```{r}

noms_by_era_partyControl = nomination_df_clean %>%
  group_by(enforcementEra, senateControlParty) %>%
  mutate(senateControlParty = recode(senateControlParty,
                                     "D" = "Democrats",
                                     "R" = "Republicans")) %>%
  summarise(Count = n(),
            Mean = round(mean(hearingMinutesInt, na.rm = T), 1),
            Median = median(hearingMinutesInt, na.rm = T),
            across(substantiveDiscussionsYes, ~(sum(., na.rm = T))),
            across(substantiveDiscussionsNo, ~(sum(., na.rm = T))),
            across(proEnforcementYes, ~(sum(., na.rm = T))),
            across(proEnforcementNo, ~(sum(., na.rm = T))),
            across(proEnforcementMixed, ~(sum(., na.rm = T)))) %>%
  ungroup() %>%
  mutate(percentSubstantive = 
           substantiveDiscussionsYes / (substantiveDiscussionsYes + substantiveDiscussionsNo)) %>%
  mutate(percentSubstantive = 100*round(percentSubstantive, 4)) %>%
  filter(!is.na(senateControlParty)) %>%
  select(enforcementEra: substantiveDiscussionsNo, 
         percentSubstantive,
         proEnforcementYes:proEnforcementMixed) %>%
  rename(`Enforcement era` = enforcementEra,
        `Party with Senate control` = senateControlParty,
         Yes = substantiveDiscussionsYes,
         No = substantiveDiscussionsNo,
         `%` = percentSubstantive,
         Pro = proEnforcementYes,
         Anti = proEnforcementNo,
         Mixed = proEnforcementMixed) #%>%
#   kable(., 
#         format = "html", 
#         caption = "Nomination hearing data by Senate control and enforcement era",
# #        booktabs = T, 
# #        linesep = "", 
#         ) %>%
#   kable_styling(full_width = T
#     #latex_options  = c("striped", "hold_position")
#     ) %>%
#   add_header_above(italic = T, c("Time period" = 2, 
#                                  " " = 1, 
#                                  "Duration of nomination \nhearings (in minutes)" = 2, 
#                      "Substantive\nantitrust\ndiscussions?" = 3, 
#                      "Attitudes\ntoward\nenforcement" = 3)) #%>%
# #column_spec(1:2, width = "2cm")
  
  
```






## Did the NYT cover nominations/hearings?
```{r}
set.seed(736)
nominationCoverage_df = nomination_df_clean %>%
  filter(nytCoverageSearched == "Yes") %>%
  mutate(Name = paste0(First_name, " ", Last_name)) %>%
  select(Name, Employer, Year_started, starts_with("nytCovered")) 


nominationCoverage_df %>%
  arrange(Year_started) %>%
  rename(Agency = Employer, 
         `Start year` = Year_started,
         `Nomination` = nytCoveredNomination,
         `Hearing` = nytCoveredHearings) %>%
  kable(caption = "Nomination hearing data by decade",
        booktabs = T, linesep = "", longtable = T) %>%
  kable_styling(latex_options  = c("striped")) %>%
  add_header_above(italic  = T, c(" " = 3, "NYT coverage of:" = 2))


```



## Flourish figures
```{r}
personnelChanges = df_summary %>%
  select(direction, `Type of positions`, count, freq, Era) %>%
  select(-count) %>%
  filter(`Type of positions` != "Other") %>%
  pivot_wider(names_from = Era,
              values_from = freq) %>% 
  select(era, direction, `Type of positions`, `Pre-1976`, `Post-1975`) %>%
  arrange(desc(direction), desc(`Type of positions`))

setwd("data/final figures")  
write_excel_csv(personnelChanges, "18_personnelChanges.xlsx")

```
```{r}
df_summary %>%
  select(direction, `Type of positions`, count, freq, Era) %>%
  select(-freq) %>%
#  filter(`Type of positions` != "Other") %>%
  pivot_wider(names_from = `Type of positions`,
              values_from = count)

# Direction - CHART OPTION
# Type of positions - X AXIS
# count OR # Freq - Y VALUES
# era - COLOR
```

