---
title: "Antitrust enforcement: SCT analysis - Final"
author: "Sima Biondi"
date: "3/31/2022"
output: pdf_document
---

```{r setupSCT, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = F, message = F)
library(knitr)
library(dplyr)
library(ggplot2)
library(readxl)
library(tidyr)
library(stringr)
library(tidyverse)
library(purrr)
library(RColorBrewer)
library(data.table)
library(rvest)
library(kableExtra)
library(scales)
library(zoo)

options(warn = -1)
fig.path = here::here("figs/final draft")

```

# Reading and cleaning data

```{r read}
sc_judge_read = read_excel("data/Supreme Court Chart.xlsx", sheet = "Business friendliness")
justice_per_court_read = read_csv("data/SCDB_2021_01_justiceCentered_Citation_sb.csv",
                             col_types = cols())
antitrust_westlaw_sc_cases_sherman = read.csv("data/03 2 2022 - post51_sct_antitrust_cases_sherman_coded.csv")

antitrust_westlaw_sc_cases_clayton = read.csv("data/03 2 2022 - post51_sct_antitrust_cases_clayton_coded.csv")

westlaw_sherman_search_df = read_csv("data/Westlaw Edge - List of 677 results for advanced (Sherman Act OR Sherman Antitrust Act).csv")

bf_scores_read = read_csv("data/Business2020_sb1.csv")


# ------ Datasets to create antitrust case dataset
#additional_cases_antitrust_read = read_csv("data/additional_cases_antitrust_sc_changed.csv")
#brannon_ginsburg_df_read = read_excel("data/brannon_ginsburg_data.xlsx")

```

```{r clean SCT cases}
antitrust_westlaw_sc_cases = antitrust_westlaw_sc_cases_sherman %>%
  mutate(statuteType = "sherman") %>%
  full_join(antitrust_westlaw_sc_cases_clayton) %>%
  mutate(statuteType = ifelse(is.na(statuteType), "clayton", statuteType)) %>%
  filter(str_detect(INCLUDE.FINAL., "[Yy]es")) %>%
  rename(includeFinal = INCLUDE.FINAL.,
         sherman1 = Sherman.1,
         sherman2 = Sherman.2,
         proAntitrustEnforcement = Pro.antitrust.enforcement) 

#setwd("/Users/simabiondi/Desktop/Posner/antitrust/data")

#antitrust_westlaw_sc_cases %>%
#  write.csv(., file = "post51_sct_antitrust_cases_final.csv")
```


```{r clean SC judges Excel}

sc_judge = sc_judge_read %>%
  mutate(year_oath = format(`Date of Oath`, "%Y")) %>%
  mutate(across(c(CC_endorse, WSJ_endorse),  na_if, "Unavailable")) %>%
  mutate(era = case_when(year_oath > 1975 ~ "Low enforcement",
                         T ~ "High enforcement")) %>%
  mutate(across(.cols = ends_with("endorse"), .fns = ~ case_when(str_detect(., "y") ~ 1, 
                                                                 T ~ 0))) %>%
  mutate(name_edit = `Last Name, First Name`) %>%
  mutate(last_name = str_extract(name_edit, "^[a-zA-Z]*")) %>%
  mutate(row_num = 1:n()) %>%
  mutate(initials = str_extract_all(name_edit, "[A-Z]")[row_num]) %>%
  mutate(middle_initial = as.character(map(initials, 3))) %>%
  mutate(first_initial = as.character(map(initials, 2))) %>%
  mutate(across(middle_initial:first_initial, ~ replace(., . == "NULL", NA))) %>%
  mutate(name_final = case_when(is.na(middle_initial) ~ paste(first_initial, last_name, sep = ""),
                                T ~ paste(first_initial, middle_initial, last_name, sep = ""))) %>%
  mutate(name_final = case_when(name_edit == "O'Connor, Sandra Day" ~ "SDOConnor",
                                name_edit == "Harlan, John Marshall" ~ "JHarlan2",
                                name_edit == "Hughes, Charles Evans" ~ "CEHughes2",
                                T ~ name_final)) %>%
  rename(justiceName = name_final) #%>%
  # #merge updated business friendliness scores into data
  # left_join(updated_bf_scores, by = "justiceName") %>%
  # select(-ELP_business_litigant_perc) %>%
  # mutate(ELP_business_litigant_perc = `fraction in favor of business`) %>%
  # #merge updated NYT business friendliness scores into data
  # left_join(select(updated_nyt_bf_scores, justiceName, total_bf_nyt_votes: bf_nyt_score), by = "justiceName") %>%
  # select(-ELP_nyt_perc, ELP_nyt_case_count) %>%
  # mutate(ELP_nyt_perc = bf_nyt_score,
  #        ELP_nyt_case_count = total_bf_nyt_votes)

```

```{r add law school to SC judge information}
page = read_html("https://en.wikipedia.org/wiki/List_of_law_schools_attended_by_United_States_Supreme_Court_justices")

listWiki = page %>% 
  html_nodes('ol') %>% 
  purrr::map(~html_nodes(.x, 'li') %>% 
        html_text() %>% 
        gsub(pattern = '\\t|\\r|\\n', replacement = '')
  )

harvardorYaleAttend = as.data.frame(listWiki[1], col.names = c("justice")) %>%
    bind_rows(  as.data.frame(listWiki[2], col.names = c("justice"))) %>%
    mutate(justice = str_remove(justice, " –.*")) %>%
    mutate(justice = str_remove(justice, " Jr.")) %>%
    mutate(lastName = str_extract(justice, "[A-z]*$"))
  

sc_judge = sc_judge %>%
  rowwise() %>%
  mutate(schoolAttended = ifelse(last_name %in% harvardorYaleAttend$lastName, 
                                 "Harvard/Yale", 
                                 "Other")) 


```


```{r clean judge vote data}
justice_per_court_raw = justice_per_court_read %>%
  select(term, justiceName, caseId) %>%
  distinct(justiceName, term, .keep_all = T) %>%
  filter(str_detect(caseId, "001")) %>%
  pivot_wider(names_from = term, values_from = caseId) %>%
  mutate(across(!justiceName, ~ case_when(!is.na(.) ~ 1, T ~ 0)))
```

```{r combine cleaned judge vote data with SC judge information }
justice_per_court =  justice_per_court_raw %>%
  left_join(sc_judge, keep = T) %>%
  rename(justiceName = justiceName.y) %>%
  select(!(`1946`:`1951`)) %>%
  filter(justiceName != "WBRutledge" &  justiceName != "FMurphy" &
           justiceName != "ACBarrett")

  
```





## Calculations

### Creating scores

#### Judge level

```{r BF and BF_NYT scores from Epstein data}
justice_bf_scores  = bf_scores_read %>%
  filter(term > 1951) %>%
  filter(BusinessLitigant == "1. business is Petitioner OR respondent") %>%
  group_by(justiceName, JVoteForBusiness) %>%
  summarise(votes = n()) %>%
  filter(!is.na(JVoteForBusiness)) %>%
  pivot_wider(names_from = JVoteForBusiness, values_from = votes) %>%
  mutate(total_votes = `j vote against business` + `j vote for business`,
         score = round(`j vote for business`/(`j vote against business` + `j vote for business`), 3)) %>%
  mutate(score_type = "bf") %>%
  rename(`pro-enforcement` = `j vote against business`,
         `anti-enforcement` = `j vote for business`) %>%
  filter(justiceName %in% justice_per_court$justiceName) 

justice_bf_nyt_scores = bf_scores_read %>%
    filter(term > 1951) %>%
  filter(BusinessLitigant == "1. business is Petitioner OR respondent" &
           nytSalience == 1) %>%
  group_by(justiceName, JVoteForBusiness) %>%
  summarise(votes = n()) %>%
  filter(!is.na(JVoteForBusiness)) %>%
  pivot_wider(names_from = JVoteForBusiness, values_from = votes) %>%
    replace(is.na(.), 0) %>%
  mutate(total_votes = `j vote against business` + `j vote for business`,
         score = round(`j vote for business`/(`j vote against business` + `j vote for business`), 3)) %>%
  mutate(score_type = "bf_nyt") %>%
  rename(`pro-enforcement` = `j vote against business`,
         `anti-enforcement` = `j vote for business`) %>%
  filter(justiceName %in% justice_per_court$justiceName) 

```

#### Court level

##### Court level by justice
```{r BF and BF_NYT score over time}

court_bf_justice_score = justice_bf_scores %>%
  left_join(select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  filter(!is.na(`1952`)) %>%
  # filter(justiceName != "ACBarrett" & justiceName != "BMKavanaugh" &
  #          justiceName != "FMurphy" & justiceName != "NMGorsuch" &
  #          justiceName != "WBRutledge") %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                           score_type == "bf" ~ .*score), .names = "{col}_bf")) %>%
  select(ends_with("_bf")) %>%
  ungroup() %>%
  summarise(across(is.numeric, ~ round(mean(., na.rm = T), 3))) %>%
  pivot_longer(everything()) %>%
  mutate(court_term = as.numeric(str_extract(name, "\\d{4}"))) %>%
  rename(bf_score = value) %>%
  select(-name)

  
court_bf_nyt_justice_score = justice_bf_nyt_scores %>%
  left_join(dplyr::select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  filter(!is.na(`1952`)) %>%
  # filter(justiceName != "ACBarrett" & justiceName != "BMKavanaugh" &
  #          justiceName != "FMurphy" & justiceName != "NMGorsuch" &
  #          justiceName != "WBRutledge") %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                           T ~ .*score), .names = "{col}_bf_nyt")) %>%
  select(ends_with("_bf_nyt")) %>%
  ungroup() %>%
  summarise(across(where(is.numeric), ~ round(mean(., na.rm = T), 3))) %>%
  pivot_longer(everything()) %>%
  mutate(court_term = as.numeric(str_extract(name, "\\d{4}"))) %>%
  rename(bf_nyt_score = value) %>%
  select(-name)

```

##### Court level by cases

```{r bf roll mean - case}
court_bf_case_scores = bf_scores_read %>%
  filter(BusinessLitigant == "1. business is Petitioner OR respondent" &
           !is.na(JVoteForBusiness)) %>%
  group_by(term, JVoteForBusiness) %>%
  summarise(votes = n()) %>%
  filter(JVoteForBusiness != "") %>%
  pivot_wider(names_from = JVoteForBusiness, values_from = votes) %>%
  mutate(total_votes = `j vote against business` + `j vote for business`,
         score = round(`j vote for business`/(`j vote against business` + `j vote for business`), 3)) %>%
  mutate(score_type = "bf") %>%
  rename(`pro-enforcement` = `j vote against business`,
         `anti-enforcement` = `j vote for business`) 
# court_bf_case_scores %>%
#   left_join(court_bf_score, by = c("term" = "court_term")) %>%
#   select(rolling_score, term, bf_score) %>%
#   pivot_longer(!term, names_to = "scoreType", values_to = "score") %>%
#   ggplot(aes(x = term, y = score, color = scoreType)) + geom_line() 
```

```{r roll mean bf_nyt - case}
court_bf_nyt_case_scores = bf_scores_read %>%
  filter(BusinessLitigant == "1. business is Petitioner OR respondent" &
           nytSalience == 1) %>%
  group_by(term, JVoteForBusiness) %>%
  summarise(votes = n()) %>%
  filter(!is.na(JVoteForBusiness)) %>%
  pivot_wider(names_from = JVoteForBusiness, values_from = votes) %>%
  replace(is.na(.), 0) %>%
  mutate(total_votes = `j vote against business` + `j vote for business`,
         score = round(`j vote for business`/(`j vote against business` + `j vote for business`), 3)) %>%
  mutate(score_type = "bf_nyt") %>%
  rename(`pro-enforcement` = `j vote against business`,
         `anti-enforcement` = `j vote for business`) 

# court_bf_nyt_justice_scores %>%
#   left_join(court_bf_nyt_score, by = c("term" = "court_term")) %>%
#   select(rolling_score, term, bf_nyt_score) %>%
#   pivot_longer(!term, names_to = "scoreType", values_to = "score") %>%
#   ggplot(aes(x = term, y = score, color = scoreType)) + geom_line() 
```


### Merging list of antitrust cases with justice votes cases

#### Creating + clean dataset of antitrust cases
```{r creating dataset with antitrust cases from SCT database}

justice_votes_per_case = justice_per_court_read %>%
  #merge list of antitrust cases with justice votes cases
  mutate(sctCite = gsub("[S]. ", "S.", sctCite)) %>%
  filter(usCite %in% filter(antitrust_westlaw_sc_cases, includeFinal == "Yes" 
                            | includeFinal == "yes")$Citation
           | sctCite %in% filter(antitrust_westlaw_sc_cases, includeFinal == "Yes" 
                            | includeFinal == "yes")$Citation) %>%
  mutate(Citation = ifelse(is.na(usCite), sctCite, usCite)) %>%
  select(voteId, dateDecision, Citation, caseName, majOpinWriter, majVotes:majority) %>%
  pivot_wider(names_from = justiceName, values_from = c(justice, vote:majority)) %>%
  group_by(Citation) %>%
  summarise(caseName = first(caseName), dateDecision = first(dateDecision), 
            majOpinWriter = mean(majOpinWriter),
            majVotes = mean(majVotes), minVotes = mean(minVotes),
            across(starts_with("vote_"), ~ mean(.x, na.rm = T))) %>%
  #add per curiam decision
  add_row(Citation = "352 U.S. 992", 
          caseName = "LAWLOR v. NATIONAL SCREEN SERVICE CORP.",
          dateDecision = "2/25/1957",
          majOpinWriter = NA,
          majVotes = 5,
          minVotes = 3,
          vote_HLBlack = 1,
          vote_SFReed = 1,
          vote_FFrankfurter = 2,
          vote_WODouglas = 1,
          vote_HHBurton = 2,
          vote_TCClark = 1,
          vote_JHarlan2 = 2,
          vote_WJBrennan = 1,
          vote_EWarren = 1) %>%
  # add handcoded court case characteristics
  left_join(., select(filter(antitrust_westlaw_sc_cases, 
                        Citation != "401 U.S. 1204"), Citation, includeFinal:sherman2),
             by = c("Citation")) #%>%
  # mutate(party1 = `party1...19`, party2 = `party2...20`, 
  #        partyDecisionFavored = `partyDecisionFavored...23`)



```



```{r integrate and clean data}

justice_votes = justice_votes_per_case %>%
  mutate(year = as.integer(str_extract(dateDecision, "[0-9]{2}$"))) %>%
  mutate(year = case_when(year < 51 & year > 9 ~ as.integer(paste0("20", year)),
                          year < 51 & year < 10 ~ as.integer(paste0("200", year)),
                          T ~ as.integer(paste0("19", year)))) %>%
  mutate(party1_comp = case_when(str_detect(party1, "[Cc]ompan") ~ 1,
                                T ~ 0)) %>%
  mutate(party2_comp = case_when(str_detect(party2, "[Cc]ompan") ~ 1,
                                T ~ 0)) %>%
  mutate(party1_gov = case_when(str_detect(party1, "[Gg]ov") ~ 1,
                                T ~ 0)) %>%
  mutate(party2_gov = case_when(str_detect(party2, "[Gg]ov") ~ 1,
                                T ~ 0)) %>%
  mutate(party1_indiv = case_when(str_detect(party1, "[Ii]ndiv") ~ 1,
                                T ~ 0)) %>%
  mutate(party2_indiv = case_when(str_detect(party2, "[Ii]ndiv") ~ 1,
                                T ~ 0)) %>%  
  mutate(party1_comp_size_big = case_when(party1_comp == 1 & str_detect(party1, "^[Bb]ig") ~ T,
                                          T ~ F)) %>%
  mutate(party2_comp_size_big = case_when(party2_comp == 1 & str_detect(party2, "^[Bb]ig") ~ T,
                                          T ~ F)) %>%
  mutate(parties_comp = case_when(party1_comp == 1 & party2_comp == 1 ~ 1,
                                  T ~ 0)) %>%
  mutate(slash_or_comp_size_unclear = case_when(str_detect(party1, "/") | str_detect(party2, "/") ~ 1,
                                                str_detect(party1, "Company") & str_detect(party2, "Company") ~ 1,
                           T ~ 0)) %>%
 # mutate(type_case_score = case_when(
    #party1_comp & party2_gov |
     #                                               party2_comp & party1_gov ~ 1,
      #                               party1_indiv & party2_comp & slash_or_comp_size_unclear == 0 |
       #                                     party2_indiv & party1_comp & slash_or_comp_size_unclear == 0 ~ 1,
      #                                      parties_comp == 1 & slash_or_comp_size_unclear == 0~ 2,
       #                              party1_gov | party2_gov ~ 3,

        #                                          T ~ 0)) %>%
  mutate(type_case_score = case_when(scoreType == "plb" ~ 2,
                                     scoreType == "govCase" ~ 1,
                                     T ~ 0)) %>%
   mutate(across(starts_with("vote_"),
                  ~ case_when(is.na(.) ~ "NA",
                            . == 1 & proAntitrustEnforcement == "Yes" ~ "pro-enforcement",
                            . == 1 & proAntitrustEnforcement == "No" ~ "anti-enforcement",
  
                            . == 2 & proAntitrustEnforcement == "Yes" ~ "anti-enforcement",
                            . == 2 &  proAntitrustEnforcement == "No" ~ "pro-enforcement",
  
                            (. == 3 | . == 4) & proAntitrustEnforcement == "Yes" ~ "pro-enforcement",
                            (. == 3 | . == 4) & proAntitrustEnforcement == "No" ~ "anti-enforcement",
  
                            (. == 6 | . == 7) & proAntitrustEnforcement == "Yes" ~ "anti-enforcement",
                            (. == 6 | . == 7) & proAntitrustEnforcement == "No" ~ "pro-enforcement",
                            #no 5s or 8s in dataset
                             T ~ "NA"),
                  .names = "dir_{.col}")) 



```

#### Calculating judge-level scores

```{r generate monopoly judge scores}


justice_monopoly_scores_raw = justice_votes %>% 
  select(starts_with("dir_vote_"), type_case_score) %>%
  pivot_longer(!type_case_score, names_to = "justice", values_to = "vote_direction") %>%
  filter(!is.na(vote_direction) & vote_direction != "NA") %>%
  group_by(justice, vote_direction, type_case_score) %>%
  summarise(count = n()) %>%
  #filter(type_case_score != 0) %>%
  pivot_wider(names_from = vote_direction, values_from = count) %>%
  mutate(across(`pro-enforcement`:`anti-enforcement`, ~ replace_na(., 0))) 


justice_monopoly_scores_anti_enforcement = justice_monopoly_scores_raw %>%
  summarise(justice = first(justice), type_case_score = 3, 
          `pro-enforcement` = sum(`pro-enforcement`),
          `anti-enforcement` = sum(`anti-enforcement`))

justice_monopoly_score = justice_monopoly_scores_raw %>%
  bind_rows(justice_monopoly_scores_anti_enforcement) %>%
  mutate(score = `pro-enforcement`/(`pro-enforcement`+ `anti-enforcement`)) %>%
  # filter(justice != "dir_vote_ACBarrett",
  #        justice != "dir_vote_BMKavanaugh",
  #        justice != "dir_vote_NMGorsuch") %>%
  filter(type_case_score != 0) %>%
  mutate(type_case_score = recode(type_case_score, 
                                  '1' = "gov_score", 
                                  '2' = "psb_score", 
                                  '3' = "pe_score")) %>%
  ungroup() %>%
  mutate(justice = str_extract(justice, "[A-Z]+[a-z]+[0-9]*")) %>%
  rename(justiceName = justice)
```



#### Court level - by justice
```{r calc court scores by justice}

court_monopoly_justice_score = justice_monopoly_score %>% 
  left_join(select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_score")) %>%
  select(justiceName, type_case_score, ends_with("score")) %>%
  filter(justiceName != "ACBarrett") %>%
  select(-score, -justiceName) %>%
  group_by(type_case_score) %>%
  summarise(across(is.numeric, ~ mean(., na.rm = T))) %>%
  pivot_longer(!type_case_score) %>%
  pivot_wider(names_from = type_case_score, values_from = value) %>%
  mutate(name = as.integer(str_extract(name, "[0-9]{4}"))) %>%
  rename(court_term = name)
```

#### Court level - by justice (without Gorsuch and Kavanaugh)
```{r calc court scores by justice without NM and BK}

court_monopoly_justice_score_ends2016 = justice_monopoly_score %>% 
  left_join(select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  mutate(score = ifelse(type_case_score %in% c("pe_score", "gov_score", "psb_score"),
                        1-score, score),
         type_case_score = case_when(type_case_score == "pe_score" ~ "ae_score",
                                     type_case_score == "gov_score" ~ "ag_score",
                                     type_case_score == "psb_score" ~ "plb_score",
                                     T ~ type_case_score)) %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_score")) %>%
  select(justiceName, type_case_score, ends_with("score")) %>%
  filter(justiceName != "ACBarrett" & justiceName != "BMKavanaugh" &
           justiceName != "NMGorsuch") %>%
  select(-score, -justiceName) %>%
  group_by(type_case_score) %>%
  summarise(across(is.numeric, ~ mean(., na.rm = T))) %>%
  pivot_longer(!type_case_score) %>%
  pivot_wider(names_from = type_case_score, values_from = value) %>%
  mutate(name = as.integer(str_extract(name, "[0-9]{4}"))) %>%
  rename(court_term = name)
```

#### Court level - by justice (anti-scores)
```{r}
court_monopoly_justice_score_anti = justice_monopoly_scores_raw %>%
  bind_rows(justice_monopoly_scores_anti_enforcement) %>%
  mutate(score = `anti-enforcement`/(`pro-enforcement`+ `anti-enforcement`)) %>%
  filter(type_case_score != 0) %>%
  mutate(type_case_score = recode(type_case_score, 
                                  '1' = "ag_score", 
                                  '2' = "plb_score", 
                                  '3' = "ae_score")) %>%
  ungroup() %>%
  mutate(justice = str_extract(justice, "[A-Z]+[a-z]+[0-9]*")) %>%
  rename(justiceName = justice) %>%
  left_join(select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_score")) %>%
  select(justiceName, type_case_score, ends_with("score")) %>%
  filter(justiceName != "ACBarrett" & justiceName != "BMKavanaugh" &
           justiceName != "NMGorsuch") %>%
  select(-score, -justiceName) %>%
  group_by(type_case_score) %>%
  summarise(across(is.numeric, ~ mean(., na.rm = T))) %>%
  pivot_longer(!type_case_score) %>%
  pivot_wider(names_from = type_case_score, values_from = value) %>%
  mutate(name = as.integer(str_extract(name, "[0-9]{4}"))) %>%
  rename(court_term = name)
```



#### Court level - by case
```{r calc court scores by case}

court_monopoly_scores_case_raw = justice_votes %>% 
  select(starts_with("dir_vote_"), type_case_score, year) %>%
  pivot_longer(!c(type_case_score, year), names_to = "justice", values_to = "vote_direction") %>%
  filter(!is.na(vote_direction) & vote_direction != "NA") %>%
  group_by(year, vote_direction, type_case_score) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = vote_direction, values_from = count) %>%
  mutate(across(`pro-enforcement`:`anti-enforcement`, ~ replace_na(., 0))) 

court_monopoly_scores_case_anti_enforcement = court_monopoly_scores_case_raw %>%
  summarise(year = first(year), type_case_score = 3, 
          `pro-enforcement` = sum(`pro-enforcement`),
          `anti-enforcement` = sum(`anti-enforcement`))

court_monopoly_case_score = court_monopoly_scores_case_raw %>%
  bind_rows(court_monopoly_scores_case_anti_enforcement) %>%
  mutate(score = `pro-enforcement`/(`pro-enforcement`+ `anti-enforcement`)) %>%
  filter(type_case_score != 0) %>%
  mutate(type_case_score = recode(type_case_score, 
                                  '1' = "gov_score", 
                                  '2' = "psb_score", 
                                  '3' = "pe_score")) 

```
### Combing all scores into 1 df

#### Names, term dates of SCT justices
```{r}
page = read_html("http://scdb.wustl.edu/documentation.php?var=majOpinWriter")

html_tbls = page %>%
  html_elements("table") %>%
  html_table()

justice_numbers_tbl = html_tbls[[6]] %>%
  rename(justiceNumber = X1, justiceName = X2, justiceDates = X3) 

justice_term_dates = justice_numbers_tbl %>%
  rowwise() %>%
  mutate(serviceStarts = str_extract_all(justiceDates, "[0-9]{4}")[[1]][[1]],
         serviceEnds = ifelse(str_detect(justiceDates, "0000"), 
                              " ",
                              str_extract_all(justiceDates, "[0-9]{4}")[[1]][2])) %>%
  mutate(termDates = case_when(
    # str_detect(serviceStarts, "19[0-9]{2}") 
    #                            & str_detect(serviceEnds, "20[0-9]{2}") ~
    #                              paste0("('", serviceStarts, "-'", serviceEnds, ")"),
                               (serviceEnds == " ") ~  
                                 paste0("('", substr(serviceStarts, 
                                                     3, 
                                                     nchar(serviceStarts)),
                                        "-", serviceEnds, ")"),
                             T ~  paste0("('", substr(serviceStarts, 3, nchar(serviceStarts)),
                                     "-'", substr(serviceEnds, 3, nchar(serviceEnds)),
                                     ")"))) 




```


#### Judge level
```{r ALL scores justice-level}

justice_scores = justice_monopoly_score %>%
  rename(score_type = type_case_score) %>%
  bind_rows(justice_bf_scores, justice_bf_nyt_scores) %>%
  left_join(select(sc_judge, Party, era, justiceName, year_oath, schoolAttended)) %>%
  mutate(total_votes = `pro-enforcement` + `anti-enforcement`) %>%
  filter(justiceName != "WBRutledge" &  justiceName != "FMurphy" & justiceName != "ACBarrett") %>%
  mutate(justiceLastName = case_when(justiceName == "SDOConnor" ~ "O'Connor",
                                     T ~ str_extract(justiceName, "[A-Z][a-z]+"))) %>%
  left_join(justice_term_dates) %>%
  mutate(justiceTitle = paste0(justiceLastName, " ", termDates))

```
#### Court level - justice
```{r ALL score court level by justice}
chiefJusticeLevels = c("Vinson", "Warren", "Burger", "Rehnquist", "Roberts")

court_justice_scores = court_monopoly_justice_score %>%
  left_join(court_bf_justice_score) %>%
  left_join(court_bf_nyt_justice_score) %>%
  ungroup() %>%
  pivot_longer(!court_term, names_to = "type_case_score", values_to = "score") %>%
  group_by(type_case_score) %>%
  mutate(rolling_score = rollmean(score, 3, align = "center", fill = 0)) %>%
  mutate(chief_term = (case_when(court_term < 1954 ~ "Vinson",
                                court_term > 1953 & court_term < 1969 ~ "Warren",
                                court_term > 1968 & court_term < 1986 ~ "Burger",
                                court_term > 1985 & court_term < 2005 ~ "Rehnquist",
                                court_term > 2004 ~ "Roberts"))) %>%
  mutate(chief_term = factor(chief_term, levels = chiefJusticeLevels))
```

#### Court level - cases
```{r ALL score court level by case}
 
court_monopoly_case_score_temp = court_monopoly_case_score %>%
  select(year, type_case_score, score) %>%
  pivot_wider(names_from = type_case_score, values_from = score) %>%
  full_join(., as.data.frame(1952:2021), by = c("year" = "1952:2021")) %>%
  left_join(rename(select(court_bf_case_scores, term, score), bf_score = score), by = c("year" = "term")) %>%
  full_join(., as.data.frame(1952:2021), by = c("year" = "1952:2021")) %>%
  left_join(rename(select(court_bf_nyt_case_scores, term, score), bf_nyt_score = score), by = c("year" = "term")) %>%
  ungroup() %>%
  pivot_longer(!year, names_to = "type_case_score", values_to = "score") %>%
  group_by(type_case_score) %>%
  mutate(rolling_score = rollapply(score, 3, mean, align = "right", fill = NA)) %>%
  mutate(decade = as.integer(paste0(str_extract(year, "[0-9]{3}"), "0"))) 

court_case_scores = court_monopoly_case_score_temp %>%
  left_join(summarise(group_by(court_monopoly_case_score_temp, decade, type_case_score),
            decadeScore = mean(score, na.rm = T))) %>%
  rename(court_term = year) %>%
  mutate(chief_term = (case_when(court_term < 1954 ~ "Vinson",
                                court_term > 1953 & court_term < 1969 ~ "Warren",
                                court_term > 1968 & court_term < 1986 ~ "Burger",
                                court_term > 1985 & court_term < 2005 ~ "Rehnquist",
                                court_term > 2004 ~ "Roberts")))

```





### Avg ae and plb of top 5 by year

```{r average AE score of top 5 per year (without NM and BK)}
court_ae_score_top5_woutGorKav = justice_monopoly_score %>%
  filter(type_case_score == "pe_score") %>%
  mutate(score = 1 - score) %>% #turn PE score to AE score
  filter(justiceName != "ACBarrett" & justiceName != "BMKavanaugh" &
           justiceName != "NMGorsuch") %>%
  left_join(select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_ae")) %>%
  select(`1952_ae`:`2019_ae`, justiceName) %>%
  mutate(across(is.numeric, ~ min_rank(desc(.x)), .names = "{col}_top")) %>%
  pivot_longer(!justiceName, names_to = "metric", values_to = "value") %>%
  mutate(term = as.integer(str_extract(metric, "[0-9]{4}")),
         type = str_extract(metric, "[a-z]{2}_?[a-z]?")) %>%
  select(-metric) %>%
  filter(!is.na(value)) %>%
  pivot_wider(names_from = type, values_from = value) %>%
  filter(ae_t < 6) %>%
  group_by(term) %>%
  summarise(mean = mean(ae, na.rm = T)) 
```

```{r average AE score of top 5 per year (ends in 2015)}
court_ae_score_top5_ends2015 = justice_monopoly_score %>%
  filter(type_case_score == "pe_score") %>%
  mutate(score = 1 - score) %>% #turn PE score to AE score
  left_join(select(justice_per_court, justiceName, `1952`:`2015`)) %>%
  mutate(across(`1952`:`2015`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_ae")) %>%
  select(`1952_ae`:`2015_ae`, justiceName) %>%
  mutate(across(is.numeric, ~ min_rank(desc(.x)), .names = "{col}_top")) %>%
  pivot_longer(!justiceName, names_to = "metric", values_to = "value") %>%
  mutate(term = as.integer(str_extract(metric, "[0-9]{4}")),
         type = str_extract(metric, "[a-z]{2}_?[a-z]?")) %>%
  select(-metric) %>%
  filter(!is.na(value)) %>%
  pivot_wider(names_from = type, values_from = value) %>%
  filter(ae_t < 6) %>%
  group_by(term) %>%
  summarise(mean = mean(ae, na.rm = T)) 
```


```{r average PLB of top 5 by year (without NM and BK)}
court_plb_score_top5_woutNMBK = justice_monopoly_score %>%
  filter(type_case_score == "psb_score") %>%
  mutate(score = 1 - score) %>%
   filter(justiceName != "ACBarrett" & justiceName != "BMKavanaugh" &
           justiceName != "NMGorsuch") %>%
  left_join(select(justice_per_court, justiceName, `1952`:`2019`)) %>%
  mutate(across(`1952`:`2019`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_plb")) %>%
  select(`1952_plb`:`2019_plb`, justiceName) %>%
  mutate(across(is.numeric, ~ min_rank(desc(.x)), .names = "{col}_top")) %>%
  pivot_longer(!justiceName, names_to = "metric", values_to = "value")  %>%
  mutate(term = as.integer(str_extract(metric, "[0-9]{4}")),
         type = str_extract(metric, "[a-z]{3}_?[a-z]?")) %>%
  select(-metric) %>%
  filter(!is.na(value)) %>%
  pivot_wider(names_from = type, values_from = value) %>%
  filter(plb_t < 6) %>%
  group_by(term) %>%
  summarise(mean = mean(plb, na.rm = T)) 

```

```{r average PLB of top 5 by year (ends in 2015)}
court_plb_score_top5_ends2015 = justice_monopoly_score %>%
  filter(type_case_score == "psb_score") %>%
  mutate(score = 1 - score) %>%
  left_join(select(justice_per_court, justiceName, `1952`:`2015`)) %>%
  mutate(across(`1952`:`2015`, ~ case_when(. == 0 ~ as.numeric(NA),
                                             T ~ .x*score), .names = "{col}_plb")) %>%
  select(`1952_plb`:`2015_plb`, justiceName) %>%
  mutate(across(is.numeric, ~ min_rank(desc(.x)), .names = "{col}_top")) %>%
  pivot_longer(!justiceName, names_to = "metric", values_to = "value")  %>%
  mutate(term = as.integer(str_extract(metric, "[0-9]{4}")),
         type = str_extract(metric, "[a-z]{3}_?[a-z]?")) %>%
  select(-metric) %>%
  filter(!is.na(value)) %>%
  pivot_wider(names_from = type, values_from = value) %>%
  filter(plb_t < 6) %>%
  group_by(term) %>%
  summarise(mean = mean(plb, na.rm = T)) 

```




## Summary mean of overall business friendliness score (bf) and business friendliness score of business-related cases appearing in the NYT (nyt)

All statistics only include justices appointed post-1945. 

### Inclusive of all cases:
```{r bf by party}

# justice_scores %>%
#   filter(score_type == "bf" | score_type == "bf_nyt") %>%
#   select(Party, score, score_type, justiceName, justiceLastName) %>%
#   pivot_wider(names_from = "score_type", values_from = "score") %>%
#   group_by(Party) %>%
#   summarise(`Business-friendliness mean` = round(mean(bf, na.rm = T), digits = 3),
#             `Business-friendliness mean of NYT cases` = round(mean(bf_nyt, na.rm = T), digits = 3))%>%
 # kable(., "latex", booktabs = T)


```

```{r}
#testing diff in parties
t_test_bf_scores = justice_scores %>%
  filter(score_type == "bf" | score_type == "bf_nyt") %>%
  select(Party, score, score_type) %>%
  group_by(Party, score_type) %>%
  summarise(val = list(score)) %>%
  pivot_wider(names_from = Party, values_from = val) %>%
  group_by(score_type) %>%
  mutate(p_value = round(t.test(unlist(D), unlist(R))$p.value, 2),
         t_value = round(t.test(unlist(D), unlist(R))$statistic, 2),
         D_mean = round(mean(unlist(D), na.rm = T), 2),
         D_sd = round(sd(unlist(D), na.rm = T), 2),
         R_mean = round(mean(unlist(R)), 2),
         R_sd = round(sd(unlist(R)), 2),
         df = round(t.test(unlist(D), unlist(R))$parameter, 2),      
         CI_lower = round(t.test(unlist(D), unlist(R))$conf.int[[1]], 2),
         CI_upper = round(t.test(unlist(D), unlist(R))$conf.int[[2]], 2),
         meanDiff = R_mean-D_mean) %>%
  select(score_type, D_mean, D_sd, R_mean, R_sd,
         t_value, df, p_value, CI_lower, CI_upper) %>%
  mutate(score_type = ifelse(score_type == "bf", "Business-friendliness", 
                             "Business-friendliness (NYT cases)")) %>%
  rename(`Type of score` = score_type,
         `Mean (D)` = D_mean,
         `SD (D)` = D_sd,
         `Mean (R)` = R_mean,
         `SD (R)` = R_sd,
         `T` = t_value,
         `Significance` = p_value,
         `Lower` = CI_lower,
         `Upper` = CI_upper) 

#namesTTest = unlist(str_split(names(t_test_bf_scores), "_"))
#names(t_test_bf_scores) = namesTTest[!(str_detect(namesTTest, "!"))]


t_test_bf_scores %>%
  kableExtra::kable("latex", booktabs = T, escape = F) %>%
  add_header_above(italic = T, c(" " = 1, "Democrats" = 2, 
                     "Republicans" = 2, 
                     " " = 3,
                     "Confidence interval" = 2))
  

```

```{r}
justice_scores %>%
  filter(score_type == "bf" | score_type == "bf_nyt") %>%
  mutate(score_type = ifelse(score_type == "bf", 
                             "All cases",
                             "Only NYT cases")) %>%
  ggplot(aes(sample = score, color = score_type)) + 
  geom_qq() + geom_qq_line() + 
  labs(x = "Theoretical quantiles", y = "Business-friendliness score", color = "Score") + 
  scale_color_grey() + theme_classic() + 
  theme(legend.position = "bottom")

ggsave(path = fig.path, "qqplot_bf_scores.png")

```



### Grouped by era:

High enforcement: 1945-1975.
Low enforcement: 1976-2019.

```{r bf by era}

t_test_bf_scores_era = justice_scores %>%
  filter(score_type == "bf" | score_type == "bf_nyt") %>%
  select(era, score, score_type, justiceName) %>%  
  group_by(era, score_type) %>%
  summarise(val = list(score)) %>%
  pivot_wider(names_from = "era", values_from = "val") %>%
  group_by(score_type) %>%
    mutate(p_value = round(t.test(unlist(`High enforcement`), 
                                  unlist(`Low enforcement`))$p.value, 2),
         t_value = round(t.test(unlist(`High enforcement`), 
                                unlist(`Low enforcement`))$statistic, 2),
         highEnforcement_mean = round(mean(unlist(`High enforcement`), na.rm = T), 2),
         highEnforcement_sd = round(sd(unlist(`High enforcement`), na.rm = T), 2),
         lowEnforcement_mean = round(mean(unlist(`Low enforcement`)), 2),
         lowEnforcement_sd = round(sd(unlist(`Low enforcement`)), 2),
         df = round(t.test(unlist(`High enforcement`), 
                           unlist(`Low enforcement`))$parameter, 2),      
         CI_lower = round(t.test(unlist(`High enforcement`), 
                                 unlist(`Low enforcement`))$conf.int[[1]], 2),
         CI_upper = round(t.test(unlist(`High enforcement`), 
                                 unlist(`Low enforcement`))$conf.int[[2]], 2),
         meanDiff = lowEnforcement_mean-highEnforcement_mean) %>%
  select(score_type, 
         highEnforcement_mean, highEnforcement_sd, lowEnforcement_mean, lowEnforcement_sd,
         t_value, df, p_value, CI_lower, CI_upper) %>%
  mutate(score_type = ifelse(score_type == "bf", "Business-friendliness", 
                              "Business-friendliness (NYT cases)")) %>%
  rename(`Type of score` = score_type,
         `Mean (high)` = highEnforcement_mean,
         `SD (high)` = highEnforcement_sd,
         `Mean (low)` = lowEnforcement_mean,
         `SD (low)` = lowEnforcement_sd,
         `T` = t_value,
         `Significance` = p_value,
         `Lower` = CI_lower,
         `Upper` = CI_upper) 

#names(t_test_bf_scores_era) = str_extract(names(t_test_bf_scores_era), "[A-z]+")

t_test_bf_scores_era %>%
  kableExtra::kable("latex", booktabs = T, escape = F) %>%
  add_header_above(italic = T, c(" " = 1, "Democrats" = 2, 
                     "Republicans" = 2, 
                     "T-test " = 3,
                     "Confidence interval" = 2))
```


### Grouped by era and party:

```{r summary of bf grouped by party and era}

justice_scores %>%
  filter(score_type == "bf" | score_type == "bf_nyt") %>%
  select(era, Party, score, score_type) %>%
  #pivot_wider(names_from = c("era", "Party"), values_from = "score") %>%
  pivot_wider(names_from = "score_type", values_from = "score") %>%
  group_by(Party, era)  %>%
  summarise(`Business-friendliness` = round(mean(unlist(bf), na.rm = T), 3),
             `Business-friendliness (NYT cases)` = round(mean(unlist(bf_nyt), na.rm = T), 3)) %>%
   rename(Era = era) %>%
   kable(., "latex", booktabs = T)

```


```{r}

# t.test(unlist(t_test_by_party_and_era$`High enforcement_D`),
#        unlist(t_test_by_party_and_era$`High enforcement_R`),
#        unlist(t_test_by_party_and_era$`Low enforcement_D`))
# 
#   mutate(p_value = round(t.test(unlist(`High enforcement_D`), 
#                                 unlist(`High enforcement_R`), 
#                                 unlist(`Low enforcement_D`),
#                                 unlist(`Low enforcement_R`))$p.value, 2),
#          t_value = round(t.test(unlist(`High enforcement_D`),
#                                 unlist(`High enforcement_R`), 
#                                 unlist(`Low enforcement_D`),
#                                 unlist(`Low enforcement_R`))$statistic, 2))
#          highEnforcement_mean = round(mean(unlist(`High enforcement`), na.rm = T), 2),
#          highEnforcement_sd = round(sd(unlist(`High enforcement`), na.rm = T), 2),
#          lowEnforcement_mean = round(mean(unlist(`Low enforcement`)), 2),
#          lowEnforcement_sd = round(sd(unlist(`Low enforcement`)), 2),
#          df = round(t.test(unlist(`High enforcement`), 
#                            unlist(`Low enforcement`))$parameter, 2),      
#          CI_lower = round(t.test(unlist(`High enforcement`), 
#                                  unlist(`Low enforcement`))$conf.int[[1]], 2),
#          CI_upper = round(t.test(unlist(`High enforcement`), 
#                                  unlist(`Low enforcement`))$conf.int[[2]], 2),
#          meanDiff = lowEnforcement_mean-highEnforcement_mean) %>%
#   select(score_type, 
#          highEnforcement_mean, highEnforcement_sd, lowEnforcement_mean, lowEnforcement_sd,
#          t_value, df, p_value, CI_lower, CI_upper) %>%
#   mutate(score_type = ifelse(score_type == "bf", "Business-friendliness", 
#                              "Business-friendliness\\\\(NYT cases)")) %>%
#   rename(`Type of score` = score_type,
#          `Mean1` = highEnforcement_mean,
#          `SD1` = highEnforcement_sd,
#          `Mean2` = lowEnforcement_mean,
#          `SD2` = lowEnforcement_sd,
#          `T` = t_value,
#          `Significance` = p_value,
#          `Lower` = CI_lower,
#          `Upper` = CI_upper) 
# 
# names(t_test_bf_scores_era) = str_extract(names(t_test_bf_scores_era), "[A-z]+")
# 
# t_test_bf_scores_era %>%
#   kableExtra::kable("html", booktabs = T, escape = F) %>%
#   add_header_above(italic = T, c(" " = 1, "Democrats" = 2, 
#                      "Republicans" = 2, 
#                      "T-test " = 3,
#                      "Confidence interval" = 2))
```



## Court scores over time
```{r 3(1) bf score over time}

court_justice_scores %>%
  filter(type_case_score == "bf_score") %>%
  ggplot() +
  geom_point(aes(x = court_term, y = score, shape = chief_term)) +
  labs(x = "Court Term", y = "Business-friendliness score (by justice)", 
       title = "Business-friendliness score of SCT by Chief Era ",
       shape = "Chief Era",
              caption = "Data from Epstein, Landes, and Posner (2013) and updated in 2020") +
  geom_label(aes(x = 1969+5, y = filter(court_justice_scores, court_term == 1969 & type_case_score == "bf_score")$score - 0.01, label = "Burger joins"), size = 3, fill = "grey90") +
    geom_label(aes(x = 1969+5, y = filter(court_justice_scores, court_term == 1969 & type_case_score == "bf_score")$score - 0.03, 
                   label = "Warren & Fortas leave"), 
               size = 3, fill = "grey90") +
  theme_classic()

ggsave(path= fig.path, "bf_score_by_sct_chief_era.png")
  
```




## Compare justice scores
```{r 8(2) justice scores (pe and psb) comparison by party}


justice_scores %>%
  left_join(select(justice_per_court, c(justiceName, Party, era, year_oath))) %>%
  filter(score_type == "pe_score" | score_type == "psb_score") %>%
  filter(!(justiceName %in% c("BMKavanaugh", "NMGorsuch"))) %>%
  select(justiceName, score_type, score, era, Party, justiceLastName, year_oath, justiceTitle) %>%
  mutate(score_type = ifelse(score_type == "psb_score", "plb_score", "ae_score"),
         score = 1 - score) %>%
  pivot_wider(names_from = score_type, values_from = score) %>%
  mutate(year_oath = as.integer(year_oath)) %>%
  group_by(Party) %>%
  arrange(Party, year_oath, justiceTitle) %>%
  mutate(order = row_number()) %>%
  pivot_longer(ae_score:plb_score) %>% 
  mutate(name = recode(name, "ae_score" = "Anti-enforcement",
                       "plb_score" = "Pro-big business")) %>%
  mutate(Party = recode(Party, 'D' = 'Democrat', 'R' = 'Republican')) %>%
  mutate(justiceTitle = fct_reorder(justiceTitle, order, .desc = T)) %>%
  ggplot() + 
 # geom_line(aes(x = value, y =  justiceTitle)) +
  geom_point(aes(x = value, y = justiceTitle, shape = name)) +
  labs(x = "Score", y = "Justice", 
      shape = "Score",
      title = "Pro-big business and anti-enforcement\n friendliness by Justice",
      caption = "Voting data from the Supreme Court Database (2021 Version 1)") + 
  theme_minimal() +
  facet_wrap(vars(Party), scales = "free_y") +   
  theme(legend.position="bottom", legend.box="vertical", legend.margin=margin(),
        axis.title.x = element_blank(), axis.title.y = element_blank()) 
  
 ggsave(path = fig.path, "sct_justice_monopoly_score_ae_plb_faceted_party.png")

```

```{r 10(1) justice scores (gov and bf) comparison by party}
justice_scores %>%
  filter(score_type == "pe_score" | score_type == "bf") %>%
  filter(!(justiceName %in% c("BMKavanaugh", "NMGorsuch"))) %>%
  select(justiceName, justiceTitle, score_type, score, Party, era, year_oath) %>%
  mutate(score_type = ifelse(score_type == "pe_score", "ae_score", "bf_score"),
         score = ifelse(score_type == "bf_score", score, 1 - score)) %>%
  pivot_wider(names_from = score_type, values_from = score) %>%
  mutate(year_oath = as.integer(year_oath)) %>%
  group_by(Party) %>%
  arrange(Party, year_oath, justiceName) %>%
  mutate(order = row_number()) %>%
  pivot_longer(ae_score: bf_score) %>%
  mutate(name = recode(name, "ae_score" = "Anti-enforcement", 
                       "bf_score" = "Business-friendliness")) %>%
  mutate(Party = recode(Party, 'D' = 'Democrat', 'R' = 'Republican')) %>%
  mutate(justiceTitle = fct_reorder(justiceTitle, order, .desc = T)) %>%
  ggplot() + 
  #geom_line(aes(x = value, y = justiceTitle)) +
  geom_point(aes(x = value, y = justiceTitle, shape = name)) +
    labs(x = "Score", y = "Justice", shape = "Score",
         title = "Business-friendliness and anti-enforcement\n scores by Justice",
                caption = "Business-friendliness data from Epstein, Landes, and Posner (2013) and updated in 2020;\nVoting data from the Supreme Court Database (2021 Version 1)") +
  theme_minimal() +
  facet_wrap(vars(Party), scales = "free_y") + 
  theme(legend.position="bottom", legend.box="vertical", legend.margin=margin(),  
        axis.title.x = element_blank(), axis.title.y = element_blank())


ggsave(path = fig.path, "sct_justice_monopoly_score_ae_bf_faceted_party.png")

```


```{r NEW justice scores (all) comparison by party}
justice_scores %>%
  filter(score_type != "bf_nyt") %>%
  filter(!(justiceName %in% c("BMKavanaugh", "NMGorsuch"))) %>%
  select(justiceName, justiceTitle, score_type, score, Party, era, year_oath) %>%
  mutate(score_type = case_when(score_type == "psb_score" ~ "plb_score",
                                score_type == "pe_score" ~ "ae_score",
                                score_type == "gov_score" ~ "ag_score",
                                T ~ "bf_score")) %>%
  mutate(score = ifelse(score_type == "bf_score", score, 1 - score)) %>%
  pivot_wider(names_from = score_type, values_from = score) %>%
  mutate(year_oath = as.integer(year_oath)) %>%
  group_by(Party) %>%
  arrange(Party, year_oath, justiceTitle) %>%
  mutate(order = row_number()) %>%
  pivot_longer(ag_score: bf_score) %>%
  mutate(name = recode(name, "ag_score" = "Anti-government", 
                       "bf_score" = "Business-friendliness",
                       "ae_score" = "Anti-enforcement",
                       "plb_score" = "Pro-big business")) %>%
  mutate(Party = recode(Party, 'D' = 'Democrat', 'R' = 'Republican')) %>%
  mutate(justiceTitle = fct_reorder(justiceTitle, order, .desc = T)) %>%
  ggplot() + 
  geom_point(aes(x = value, y = justiceTitle, shape = name)) +
    labs(x = "Score", y = "Justice", shape = "Score",
         title = "All scores by Justice", 
         caption = "Business-friendliness data from Epstein, Landes, and Posner (2013) and updated in 2020;\nVoting data from the Supreme Court Database (2021 Version 1)")+ 
  theme_minimal() +
  facet_wrap(vars(Party), scales = "free_y") + 
  theme(legend.position="bottom", legend.box="vertical", 
        axis.title.x = element_blank(), axis.title.y = element_blank()) + 
  guides(shape=guide_legend(ncol=2))


ggsave(path = fig.path, "sct_justice_monopoly_score_all_faceted_party.png")
```

## Comparing court scores over time

```{r 12(1) pe/psb/pg over time figures (by year justice) - Kavanaugh and Gorsuch removed}

#court_justice_scores %>%
  
court_monopoly_justice_score_ends2016 %>%
  pivot_longer(!court_term, names_to = "type_case_score", values_to = "score") %>%
  filter(type_case_score == "ae_score" |  
           type_case_score == "plb_score" |  
           type_case_score == "ag_score") %>%
  mutate(type_case_score = recode(type_case_score, "ae_score" = "Anti-enforcement",
                              "plb_score" = "Pro-big business",
                              "ag_score" = "Anti-goverment")) %>%
  ggplot() + 
  geom_line(aes(x = court_term, y = score, color = type_case_score)) +
 #     scale_color_grey(start = 0.25, end = 0.75) + 
  theme_classic() +
      scale_color_grey(start = 0, end = 0.8) + 
  labs(x = "Court Term", y = "Moving average score",
       title = "Moving average measures of the Court's anti-enforcement,\nanti-government, and pro-big company bias over\ntime (by justice profile)",
       color = "Score",
      caption = "Voting data from the Supreme Court Database (2021 Version 1)") +   
  theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) 

ggsave(path = fig.path, "court_monopoly_justice_score_ends2016.png")

```
```{r 12(1) pe/psb/pg over time figures (by year justice) - excludes 2016}

court_monopoly_justice_score_anti %>%
  filter(court_term < 2016) %>%
  pivot_longer(!court_term, names_to = "type_case_score", values_to = "score") %>%
  mutate(type_case_score = recode(type_case_score, "ae_score" = "Anti-enforcement",
                              "plb_score" = "Pro-big business",
                              "ag_score" = "Anti-goverment")) %>%
  ggplot() + 
  geom_line(aes(x = court_term, y = score, color = type_case_score)) +
 #     scale_color_grey(start = 0.25, end = 0.75) + 
  theme_classic() +
    scale_color_grey(start = 0, end = 0.8) + 
  labs(x = "Court Term", y = "Moving average score",
       title = "Moving average measures of the Court's pro-enforcement, pro-government,\n and pro-small company bias over time (by justice profile)",
       color = "Score",
      caption = "Voting data from the Supreme Court Database (2021 Version 1)") +  
  theme(legend.position="bottom", legend.box="vertical", legend.margin=margin()) 

ggsave(path = fig.path, "court_monopoly_justice_score_anti.png")


```


```{r 15(1) average of top 5 graphs (w/out NM and BK)}


court_ae_score_top5_woutGorKav %>%
  left_join(court_plb_score_top5_woutNMBK, by = "term", suffix = c("_ae", "_plc")) %>%
  pivot_longer(!term, names_to = "mean_type", values_to = "mean") %>%
  mutate(mean_type = case_when(mean_type == "mean_ae" ~ "Anti-enforcement",
                               T ~ "Pro-big company")) %>%
  ggplot(aes(x = term, y = mean, color = mean_type)) + 
  #geom_point() + 
  geom_line() +
  scale_color_grey(start = 0.1, end = 0.5) + 
  theme_classic() +
  labs(x = "Court Term", y = "Mean", 
       title = "Moving average of the top five anti-enforcement and pro-big\n company scores over SCT terms",
       color = "Score",
      caption = "Voting data from the Supreme Court Database (2021 Version 1)") +
  theme(legend.position = "bottom")

ggsave(path = fig.path, "court_ae_score_top5_woutGorKav.png")


```


```{r 15(1) average of top 5 graphs (ends after 2015)}


court_ae_score_top5_ends2015 %>%
  left_join(court_plb_score_top5_ends2015, by = "term", suffix = c("_ae", "_plc")) %>%
  pivot_longer(!term, names_to = "mean_type", values_to = "mean") %>%
  mutate(mean_type = case_when(mean_type == "mean_ae" ~ "Anti-enforcement",
                               T ~ "Pro-big company")) %>%
  ggplot(aes(x = term, y = mean, color = mean_type)) + 
  #geom_point() + 
  geom_line() +
  scale_color_grey(start = 0.1, end = 0.5) + 
  theme_classic() +
  labs(x = "Court Term", y = "Mean", 
       title = "Moving average of top five anti-enforcement and pro-big\n company scores over SCT terms",
       color = "Score",
      caption = "Voting data from the Supreme Court Database (2021 Version 1)") +
  theme(legend.position = "bottom")

ggsave(path = fig.path, "court_ae_score_top5_ends2015.png")


```


## Expanding to diminishing enforcement ratio (win-loss) graphs
```{r 19(1) antitrust enforcement all cases}

#bar chart
antitrust_westlaw_sc_cases %>%
  select(year, proAntitrustEnforcement) %>%
  mutate(proAntitrustEnforcement_f = forcats::fct_rev(proAntitrustEnforcement)) %>%
  ggplot() + 
  geom_bar(aes(x = year, fill = proAntitrustEnforcement_f), position = "stack") + 
  scale_fill_manual(values = c("Yes" = "green4", "No" = "red")) + 
  theme_classic() + theme(legend.position = "bottom") +
  labs(title = "Expanding to diminishing enforcement ratio of Supreme Court\nantitrust cases", 
       x = "Court Term",
       y = "Count",
       fill = "Expands enforcement?") +
    scale_y_continuous(breaks= breaks_pretty()) 

ggsave(path = fig.path, "win_loss_ratio.png")


```

## Pro-enforcement score of majority opinion authors
```{r 14(1) pe of majOpinWriter}

justice_votes %>%
  select(majOpinWriter, year) %>%
  filter(!is.na(majOpinWriter)) %>%
  inner_join(justice_numbers_tbl, by = c("majOpinWriter" = "justiceNumber")) %>%
  left_join(filter(justice_scores, score_type == "pe_score"), by = "justiceName") %>%
  filter(!is.na(score_type)) %>% #Kavanaugh and Gorsuch don't have bf or psb score
  group_by(year) %>%
  summarise(year = mean(year), score = mean(score, na.rm = T)) %>%
  filter(year < 2019) %>%
  ggplot(aes(x = year, y = score)) + 
  geom_smooth(color = "black", method = "lm") + 
  geom_point() + 
  labs(x = "Court Term", y = "Mean",
           title = "Mean pro-enforcement scores of SCT opinion authors over time",
      caption = "Authorship and voting data from the Supreme Court Database (2021 Version 1)") +
  theme_classic()

ggsave(path = fig.path, "pe_score_SCT_opinion_authors.png")


```

## School attended and average justice scores
```{r}
justice_scores %>%
  mutate(score_type = case_when(score_type == "bf" ~ "Business friendliness",
                                score_type == "bf_nyt" ~ "NYT business friendliness",
                                score_type == "gov_score" ~ "Pro-government",
                                score_type == "pe_score" ~ "Pro-enforcement score",
                                T ~ "Pro-small business score")) %>%
  group_by(score_type, schoolAttended) %>%
  summarise(score_type = first(score_type),
            score = round(mean(score), 3),
            schoolAttended = first(schoolAttended)) 

justice_scores %>%
  mutate(score_type = case_when(score_type == "bf" ~ "Business friendliness",
                                score_type == "bf_nyt" ~ "NYT business friendliness",
                                score_type == "gov_score" ~ "Pro-government",
                                score_type == "pe_score" ~ "Pro-enforcement score",
                                T ~ "Pro-small business score")) %>%
  select(justiceName, score_type, score, schoolAttended) %>%
  ggplot(aes(x = score_type, y = score, fill = schoolAttended)) + 
           geom_boxplot() + facet_wrap(~score_type, scale = "free")

ggsave(path = fig.path, "justice_scores_by_school.png")
  
```

## Flourish data prep

### Fig 10: violin plot
```{r violin plot 19(1) antitrust enforcement all cases}

#bar chart
sctCaseEnforcement = antitrust_westlaw_sc_cases %>%
  select(year, proAntitrustEnforcement, Title) %>%
 # mutate(count = 1)
#%>%
  group_by(year, proAntitrustEnforcement) %>%
  summarise(count = n()) %>%
#%>%
 # mutate(year_c = as.character(year))
#%>%
  pivot_wider(names_from = proAntitrustEnforcement, values_from = count) %>%
  mutate(across(No:Yes, ~replace_na(., 0)))
         No = No*-1) %>%
  mutate(mean = mean(c(No, Yes))) %>%
  pivot_longer(!year)
  


setwd("data/final figures")  
write_excel_csv(sctCaseEnforcement, "10_sctCaseEnforcement.xlsx")

```

### Fig 11: bf score over time

```{r flourish 3(1) bf score over time}

sctBF_court_score = court_justice_scores %>%
  filter(type_case_score == "bf_score") %>%
  ungroup() %>%
  select(court_term, score, chief_term) %>%
  pivot_wider(names_from = court_term, values_from = c(chief_term)) 
  pivot_longer(everything())
  pivot_wider(names_from = court_term, 
              values_from = c(score, chief_term),
              names_glue = "{variable}_{.value}_n") 
  select(-type_case_score) %>%
  pivot_longer(ends_with("_n"))

#setwd("data/final figures")  
#write_excel_csv(sctBF_court_score, "11_sctBF_court_score.xlsx")

```
### Fig 12: top 5 scores
```{r flourish 15(1) average of top 5 graphs (ends after 2015)}


top5score_court = court_ae_score_top5_ends2015 %>%
  left_join(court_plb_score_top5_ends2015, by = "term", suffix = c("_ae", "_plc")) %>%
  pivot_longer(!term, names_to = "mean_type", values_to = "mean") %>%
  mutate(mean_type = case_when(mean_type == "mean_ae" ~ "Anti-enforcement",
                               T ~ "Pro-big company")) %>%
  pivot_wider(names_from = mean_type, values_from = mean)

#setwd("data/final figures")  
#write_excel_csv(top5score_court, "12_top5score_court.xlsx")


```

### Fig 13: justice AE and BF scores

```{r flourish 10(1) justice scores (gov and bf) comparison by party}
sctJusticeAEscores = justice_scores %>%
  filter(score_type == "pe_score" | score_type == "bf") %>%
  filter(!(justiceName %in% c("BMKavanaugh", "NMGorsuch"))) %>%
  select(justiceName, justiceTitle, score_type, score, Party, era, year_oath) %>%
  mutate(score_type = ifelse(score_type == "pe_score", "ae_score", "bf_score"),
         score = ifelse(score_type == "bf_score", score, 1 - score)) %>%
  pivot_wider(names_from = score_type, values_from = score) %>%
  mutate(year_oath = as.integer(year_oath)) %>%
  group_by(Party) %>%
  arrange(Party, year_oath, justiceName) %>%
  mutate(order = row_number()) %>%
  pivot_longer(ae_score: bf_score) %>%
  mutate(name = recode(name, "ae_score" = "Anti-enforcement", 
                       "bf_score" = "Business-friendliness")) %>%
  mutate(Party = recode(Party, 'D' = 'Democrat', 'R' = 'Republican')) %>%
  mutate(justiceTitle = fct_reorder(justiceTitle, order, .desc = T)) %>%
  arrange(year_oath) %>%
  mutate(justiceTitleLastName = str_remove(justiceTitle, "\\(.*"))
#%>%
 # pivot_wider(names_from = name, values_from = value)


setwd("data/final figures")  
write_excel_csv(sctJusticeAEscores, "13_sctJusticeAEscores.xlsx")


```

### Fig 14: courtPLBandAG_scores
```{r flourish 12(1) pe/psb/pg over time figures (by year justice) - excludes 2016}

courtPLBandAG_scores = court_monopoly_justice_score_anti %>%
  filter(court_term < 2016) %>%
  pivot_longer(!court_term, names_to = "type_case_score", values_to = "score") %>%
  filter(type_case_score != "ae_score") %>%
  mutate(type_case_score = recode(type_case_score, 
                                  #"ae_score" = "Anti-enforcement",
                              "plb_score" = "Pro-big business",
                              "ag_score" = "Anti-goverment")) %>%
  pivot_wider(names_from = type_case_score, values_from = score)



setwd("data/final figures")  
write_excel_csv(courtPLBandAG_scores, "14_scourtPLBandAG_scores.xlsx")


```


### Fig 16: justice AE and PLB scores
```{r flourish 8(2) justice scores (pe and psb) comparison by party}


sctJusticeAE_PLBscores = justice_scores %>%
  left_join(select(justice_per_court, c(justiceName, Party, era, year_oath))) %>%
  filter(score_type == "pe_score" | score_type == "psb_score") %>%
  filter(!(justiceName %in% c("BMKavanaugh", "NMGorsuch"))) %>%
  select(justiceName, score_type, score, era, Party, justiceLastName, year_oath, justiceTitle) %>%
  mutate(score_type = ifelse(score_type == "psb_score", "plb_score", "ae_score"),
         score = 1 - score) %>%
  pivot_wider(names_from = score_type, values_from = score) %>%
  mutate(year_oath = as.integer(year_oath)) %>%
  group_by(Party) %>%
  arrange(Party, year_oath, justiceTitle) %>%
  mutate(order = row_number()) %>%
  pivot_longer(ae_score:plb_score) %>% 
  mutate(name = recode(name, "ae_score" = "Anti-enforcement",
                       "plb_score" = "Pro-big business")) %>%
  mutate(Party = recode(Party, 'D' = 'Democrat', 'R' = 'Republican')) %>%
  mutate(justiceTitle = fct_reorder(justiceTitle, order, .desc = T)) %>%
  mutate(justiceLastName = str_remove(justiceTitle, "\\(.*")) %>%
  arrange(year_oath) %>%
  mutate(test = paste(Party, "-", name))


setwd("data/final figures")  
write_excel_csv(sctJusticeAE_PLBscores, "16_sctJusticeAE_PLBscores.xlsx")

```

