---
title: "Personnel summary statistics"
author: "Sima Biondi"
date: "5/7/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F)
library(ggplot2)
library(dplyr)
library(tidyr)
library(finalfit)
library(gridExtra)
```


# Summary statistics - 
## What this document does:
### 1. Create new variables: length_of_tenure, age_at_appointment
### 2. Presents the distributions of key variables: Administration_appointee, party_affiliation, Education, Type of previous position, generalized_previous_experience,   following_position, generalized_following_exp, appointment_age
### 3. Compares previous and following positions
### 4. Check for missing data

# Set up
```{r}
setwd("~/Desktop/Posner/antitrust") 
```


## Load and clean data
```{r} 
df = read.csv("Part_2_v3.csv", stringsAsFactors = F) 
df[is.na(df)] = 0
df = df %>%
  select(-Source, -Source2, -Source3, -Notes, -Appointment_age, -Appointment_age_rounded) #remove cols
```


## Create new variable: time_period, length of tenure, appointment age
```{r}
df = df %>%
  mutate(time_period = ifelse(Year_started < 1976, "pre", "post")) %>%
  mutate(length_of_tenure = ifelse(Year_ended-Year_started > 0, Year_ended-Year_started, NA)) %>%
  mutate(age_at_appoint = ifelse(Year_started-Birth_year < 100, Year_started-Birth_year, NA)) #removing unknown DOBs from calc
```


## Basic summary statistics
```{r}
summary(select(df, -First_name, -Middle_name, -Last_name, -Suffix, -FTC_seat, -Education, -Previous_position,
               -Generalized_previous_experience, -Following_position, -Generalized_following_experience))
```

## Summary graphics and tables

### Year started, Year ended, admin appointee, party affiliation
```{r}
#Year started
ggplot(df, aes(x=Year_started)) + geom_histogram(binwidth = 10) + labs(title = "Start year of appointees over time") + xlab("Year")

#Year ended
a = subset(df, Year_ended > 100)
ggplot(a, aes(x=Year_ended)) + geom_histogram(binwidth = 10) + labs(title = "End year of term over time") + xlab("Year")

#Administration appointee
table(df$Administration_appointee)

#Party_affiliation
table(df$Party_affiliation)

table(subset(df, Year_started < 1976)$Party_affiliation)
table(subset(df, Year_started > 1975)$Party_affiliation)
prop.table(table(df$Party_affiliation))

```

### Summary graphics continued: age, length of tenure, law firms mentioned
```{r}
# Age
ggplot(df, aes(x = age_at_appoint)) + geom_histogram(binwidth = 10) + geom_vline(aes(xintercept = mean(age_at_appoint, na.rm = T)), 
  color = "red") + labs(title = "Distribution of officials' age at time of appointment") + xlab("Age")
ggplot(df[df$Year_started < 1976,], aes(x = age_at_appoint)) + 
  geom_histogram(binwidth = 10) + geom_vline(aes(xintercept = mean(age_at_appoint, na.rm = T)), color = "blue") + 
   labs(title = "Distribution of officials' age at time of appointment") + xlab("Age")
ggplot(df[df$Year_started >1975,], aes(x = age_at_appoint)) + geom_histogram(binwidth = 10) + 
  geom_vline(aes(xintercept = mean(age_at_appoint, na.rm = T)), color = "green") +  
  labs(title = "Distribution of officials' age at time of appointment") + xlab("Age")
         
df_age_mean = df %>%
  group_by(time_period) %>%
  summarise(age_mean = mean(age_at_appoint, na.rm = T))
ggplot(df, aes(x = age_at_appoint, fill = time_period)) + geom_histogram(binwidth = 5, alpha=.5, position="identity") + 
  geom_vline(data = df_age_mean, aes(xintercept = age_mean, color = time_period), linetype = "dashed", size = 1) + 
    labs(title = "Distribution of officials' age at time of appointment (not adjusted)") + xlab("Age") 

#Adjusted for age calc
df_age_adjusted = df %>%
  mutate(age_at_appoint_adjusted = ifelse(time_period == "pre", age_at_appoint *1.12, age_at_appoint))
df_age_adjusted_mean = df_age_adjusted %>%
  group_by(time_period) %>%
  summarise(age_adj_mean = mean(age_at_appoint_adjusted, na.rm = T))
ggplot(df_age_adjusted, aes(x = age_at_appoint_adjusted, fill = time_period)) + geom_density(alpha = 0.3) +  
  geom_vline(data = df_age_adjusted_mean, aes(xintercept = age_adj_mean, color = time_period), linetype = "dashed", size = 1) + 
    labs(title = "Distribution of officials' age at time of appointment (adjusted)") + xlab("Age") 

#Difference in age (not adjusted)
mean(df$age_at_appoint, na.rm = T)
mean(subset(df, Year_started < 1976)$age_at_appoint, na.rm = T) - mean(subset(df, Year_started > 1975)$age_at_appoint, na.rm = T)
```

```{r}

#Length of tenure
ggplot(df, aes(x = length_of_tenure)) + geom_histogram(binwidth = 5) +
  labs(title = "Distribution of officials' length of tenure") + xlab("Length of term (in years)") 

df_tenure_mean = df %>%
  group_by(time_period) %>%
  summarise(tenure_mean = mean(length_of_tenure, na.rm = T))

ggplot(df, aes(x = length_of_tenure, fill = time_period)) + geom_histogram(binwidth = 5, alpha=.5, position="identity") +
  geom_vline(data = df_tenure_mean, aes(xintercept = tenure_mean, color = time_period), linetype = "dashed", size = 1) +   
  labs(title = "Distribution of officials' length of tenure") + xlab("Length of term (in years)") 


#Law firms where officials found jobs after leaving government 
table(df$Following_law_firms)
```


## Comparing previous and following positions

### Calculations: altering datasets to simplifying groupings, calculating counts/percents per group, comboing and cleaning
```{r}
####################### simplifying groupings (reduce categories of type of job)
df = df %>%
  mutate(prev_position_simp = 
           ifelse(grepl("Law firm|Industry|Private practice|Journalist", Type_of_previous_position), "Private sector", 
                  ifelse(grepl("Government|Academia", Type_of_previous_position), "Public sector and academia", "Other"))) %>%
  mutate(prev_position_simp = as.factor(prev_position_simp)) %>%
  mutate(follow_position_simp = 
           ifelse(grepl("Law firm|Industry|Private practice|Journalist", Type_of_following_position), "Private sector", 
                  ifelse(grepl("Government|Academia", Type_of_following_position), "Public sector and academia", "Other"))) %>%
  mutate(follow_position_simp = as.factor(follow_position_simp))

####################### calculating counts/percents of each type
previous_position_df = df %>%
  select(prev_position_simp, time_period) %>%
  group_by(time_period) %>%
  count(prev_position_simp) %>%
  mutate(percent = ifelse(time_period == "pre", n/nrow(subset(df, time_period == "pre")), 
         n/nrow(subset(df, time_period == "post"))))

following_position_df = df %>%
  select(follow_position_simp, time_period) %>%
  group_by(time_period) %>%
  count(follow_position_simp) %>%
  mutate(percent = ifelse(time_period == "pre", n/nrow(subset(df, time_period == "pre")), 
                          n/nrow(subset(df, time_period == "post"))))

####################### Set colors
#table(df$prev_position_simp)
sectionColors = setNames(gray.colors(3), c("Private sector", "Public sector and academia", "Other"))

####################### Combine frequency tables
freq_table_all = data_frame() %>%
  bind_rows(previous_position_df, following_position_df) %>%
  mutate(timing = ifelse(is.na(prev_position_simp), "Following Position", "Previous Position")) %>%
  mutate(timing_f = factor(timing, levels = c("Previous Position", "Following Position"))) %>%
  mutate(time_period = ifelse(grepl("pre", time_period), "Pre-1976", "Post-1975")) %>%
  mutate(time_period_f = factor(time_period, levels = c("Pre-1976", "Post-1975"))) %>%
  mutate(position = coalesce(prev_position_simp, follow_position_simp)) %>%
  select(-prev_position_simp, -follow_position_simp) 
```

### Graphical representations
```{r}

# 4x4 of change in timing and time_period
p1_all = ggplot(freq_table_all, aes(x="", y = percent, fill = position)) + 
  geom_bar(stat = "identity", width = 1, color = "black") + coord_polar("y") + theme_void() +   scale_fill_manual(values = sectionColors)
p1_all + facet_grid(timing_f ~ time_period_f)

#previous jobs breakdown pre and post
p1_prev = ggplot(subset(freq_table_all, timing_f == "Previous Position"), aes(x="", y = percent, fill = position)) +   
  geom_bar(stat = "identity", width = 1, color = "black") + coord_polar("y") + theme_void() + 
  scale_fill_manual(values = sectionColors, name="Type of position", 
                    breaks = c("Private sector", "Public sector and academia", "Other"), 
                    labels = c("Private sector", "Public sector and academia", "Other")) + 
  labs(title = "Comparing the composition of officials' prior position", subtitle = "Initial position before joining government post\n", caption = "Based on data from: Wikipedia, Congress.gov, and alternate sources" )
p1_prev + facet_grid(cols = vars(time_period_f))
setwd("~/Desktop/Posner/antitrust/Graphs")
ggsave("pie_chart_previous_position_across_time_period.pdf", width = 14, height = 7)


#following jobs breakdown pre and post
p1_follow = ggplot(subset(freq_table_all, timing_f == "Following Position"), aes(x="", y = percent, fill = position)) +   
  geom_bar(stat = "identity", width = 1, color = "black") + coord_polar("y") + theme_void() + 
  scale_fill_manual(values = sectionColors, name="Type of position", 
                    breaks = c("Private sector", "Public sector and academia", "Other"), 
                    labels = c("Private sector", "Public sector and academia", "Other")) + 
  labs(title = "Comparing the composition of officials' following position", subtitle = "Initial position after leaving government post\n", caption = "Based on data from: Wikipedia, Congress.gov, and alternate sources" )
p1_follow + facet_grid(cols = vars(time_period_f))
setwd("~/Desktop/Posner/antitrust/Graphs")
ggsave("pie_chart_following_position_across_time_period.pdf", width = 14, height = 7)

```



## Missing data
```{r}
df %>% missing_plot()
```
